---
title: "Exercise Measure Development PCA"
date: "`r format(Sys.time(), '%m/%d/%y')`"
output: 
  html_document: 
    theme: yeti 
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
.libPaths(Sys.getenv("R_LIBS_USER"))

knitr::opts_chunk$set(echo = TRUE)

# detach all libraries

detachAllPackages <- function() {
  basic.packages <- c("package:stats", "package:graphics", "package:grDevices", "package:utils", "package:datasets", "package:methods", "package:base")
  package.list <- search()[ifelse(unlist(gregexpr("package:", search()))==1, TRUE, FALSE)]
  package.list <- setdiff(package.list, basic.packages)
  if (length(package.list)>0)  for (package in package.list) detach(package,  character.only=TRUE)
}
detachAllPackages()

# function to load libraries

pkgTest <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[,  "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg,  dependencies = TRUE)
  sapply(pkg,  require,  character.only = TRUE)
}

# knitr

knitr::knit_hooks$set(output = function(x, options){
  if(!is.null(options$max_height)){
    paste('<pre style = "max-height:', options$max_height, '; float: left; width: 910px; overflow-y: auto;">', x, "</pre>", sep = "")
  }else{
    x
  }
  
})

# loading packages 
lapply(c("tidyverse"),pkgTest)
lapply(c("readr"),pkgTest)
lapply(c("paletteer"),pkgTest)
lapply(c("kableExtra"),pkgTest)
library(tidyverse)
library(readr)
library(paletteer)
library(kableExtra)
```

```{r, include=FALSE}
options(width = 60)
local({
  hook_output <- knitr::knit_hooks$get('output')
  knitr::knit_hooks$set(output = function(x, options) {
    if (!is.null(options$max.height)) options$attr.output <- c(
      options$attr.output,
      sprintf('style="max-height: %s;"', options$max.height)
    )
    hook_output(x, options)
  })
})
```

```{css, echo=FALSE}
<style type="text/css">

body, td {
   font-size: 14px;
}
code.r{
  font-size: 12px;
}
pre {
  font-size: 12px
}
</style>
```

```{css, echo=FALSE}
  #TOC {
    max-width: fit-content;
    white-space: nowrap;
  }
  
  div:has(> #TOC) {
    display: flex;
    flex-direction: row-reverse;
}
```

### Importing Data  

```{r}

setwd("/Users/carolinelee/Desktop/MIAU-exer-FA")

Community_Overall_Sample <- read_csv("Exercise_Com_Overall.csv")

MTurk_Overall_Sample <- read_csv("Exercise_MTurk_Overall.csv")

SMU_Overall_Sample <- read_csv("Exercise_SMU_Overall.csv")
```

### Compiling Data 

```{r, results='asis'}
ComMTurk_Overall_Sample <- merge(Community_Overall_Sample, MTurk_Overall_Sample, by = "Item_No", all.x = TRUE)

Combined_Overall_Sample <- merge(ComMTurk_Overall_Sample, SMU_Overall_Sample, by = "Item_No", all.x = TRUE)
```

### Analysis For Red Pos/Neg Valence Factors 

```{r, results='asis'}
Combined_Overall_PN <- Combined_Overall_Sample[ ,c(1, 2:4, 9:10, 16:18)]

Combined_PN_NoNum <- Combined_Overall_PN[,-1]

Combined_Overall_PN$LoadedFactor <- apply(Combined_PN_NoNum, 1, function(i) paste(colnames(Combined_PN_NoNum)[!is.na(i) ], collapse = ", "))

function1 <- function(x) {
  count.fields(textConnection(Combined_Overall_PN$LoadedFactor[x]), sep = ",", blank.lines.skip = FALSE)
}

tbl1 <- as.data.frame(table(function1(1:312)))

knitr::kable(tbl1)
```

```{r}
FL_count_PN <- as.list(function1(1:312)) # number of factor loadings per item 

### ZERO FACTOR LOADINGS ###

# red list, items that did not load on any factor =========================== RED 1 START

zeroFL_PN <- which(FL_count_PN == 0)

# =========================================================================== RED 1 END

### ONE FACTOR LOADING ###

oneFL_PN <- which(FL_count_PN == 1) # subsetting for items that loaded on one factor only

oneFL_df_PN <- Combined_Overall_PN[oneFL_PN, ]

oneFL_df_PN$loadedFL <- apply(oneFL_df_PN[,-1], 1, function(z) na.omit(z)[1])

oneFL_df_PN$loadedFL <- as.numeric(oneFL_df_PN$loadedFL)

# green list, items that loaded >=.4 & <.75 on one factor ================== YELLOW 1 START

oneFL_inrange_PN <- which(abs(oneFL_df_PN$loadedFL)>= .40 & abs(oneFL_df_PN$loadedFL) < .75)

oneFL_inrange_PN <- oneFL_df_PN[oneFL_inrange_PN, ]

oneFL_inrange_items_PN <- oneFL_inrange_PN$Item_No 

# ========================================================================== YELLOW 1 END

# orange  list, items that loaded on one factor only but with <.4 or >=.75 loading == ORANGE 1 START

oneFL_notir_PN <- which(abs(oneFL_df_PN$loadedFL) < .40 | abs(oneFL_df_PN$loadedFL) >= .75)

oneFL_notir_PN <- oneFL_df_PN[oneFL_notir_PN, ]

oneFL_notir_items_PN <- oneFL_notir_PN$Item_No

# ================================================================================== ORANGE 1 END

### TWO FACTOR LOADINGS 

twoFL_PN <- which(FL_count_PN == 2) # subsetting for items that loaded on two factors

twoFL_df_PN <- Combined_Overall_PN[twoFL_PN, ]

tbl2 <- as.data.frame(table(twoFL_df_PN$LoadedFactor))

knitr::kable(tbl2)
```

```{r}
twoFL_notsplit_PN <- with(twoFL_df_PN, which(LoadedFactor %in% c("Com_F1_PosVal, MTurk_F1_PosVal", "Com_F1_PosVal, SMU_F1_CogPosVal", "Com_F1_PosVal, SMU_F2_PhysPosVal", "Com_F2_BroadPos, MTurk_F1_PosVal", "Com_F3_NegVal, MTurk_F2_Negval", "MTurk_F1_PosVal, SMU_F1_CogPosVal", "MTurk_F1_PosVal, SMU_F2_PhysPosVal", "MTurk_F2_Negval, SMU_F3_BroadNegVal")))

twoFL_notsplit_PN <- twoFL_df_PN[twoFL_notsplit_PN, ]

twoFL_notsplit_NoNum_PN <- twoFL_notsplit_PN[,-c(1, 10)] # removing non-numerical columns

twoFL_notsplit_PN$firstloading <- apply(twoFL_notsplit_NoNum_PN, 1, function(z) na.omit(z)[1]) # extract first loading 

twoFL_notsplit_PN$firstloading <- as.numeric(twoFL_notsplit_PN$firstloading)

twoFL_notsplit_PN$secondloading <- apply(twoFL_notsplit_NoNum_PN, 1, function(z) na.omit(z)[2]) # extract second loading 

twoFL_notsplit_PN$secondloading <- as.numeric(twoFL_notsplit_PN$secondloading)

twoFL_notsplit_PN$firstFL_inrange <- ifelse(abs(twoFL_notsplit_PN$firstloading) >= .40 & abs(twoFL_notsplit_PN$firstloading) < .75, TRUE, FALSE)

twoFL_notsplit_PN$secondFL_inrange <- ifelse(abs(twoFL_notsplit_PN$secondloading) >= .40 & abs(twoFL_notsplit_PN$secondloading) < .75, TRUE, FALSE)

# no cross-loadings within sample, so no red
twoFL_notsplit_PN$category <- ifelse(twoFL_notsplit_PN$firstFL_inrange == TRUE & twoFL_notsplit_PN$secondFL_inrange == TRUE, "YELLOW", "ORANGE")

# items that loaded in range in two different samples (both pos or both neg) = YELLOW 2 START

twoFL_YELLOW_PN <- with(twoFL_notsplit_PN, which(category %in% "YELLOW"))

twoFL_YELLOW_PN <- twoFL_notsplit_PN[twoFL_YELLOW_PN, ]

twoFL_YELLOW_items_PN <- twoFL_YELLOW_PN$Item_No 

# ========================================================================= YELLOW 2 END 

# non-split items that were in range in only one or out of range in both == ORANGE 2 START

twoFL_ORANGE_PN <- with(twoFL_notsplit_PN, which(category %in% "ORANGE"))

twoFL_ORANGE_PN <- twoFL_notsplit_PN[twoFL_ORANGE_PN, ]

twoFL_ORANGE_items_PN <- twoFL_ORANGE_PN$Item_No 

# ========================================================================= ORANGE 2 END 

# orange list, items that split within or across samples but not in range = ORANGE 3 START

twoFL_split_PN <- with(twoFL_df_PN, which(LoadedFactor %in% c("Com_F2_BroadPos, MTurk_F2_Negval", "Com_F3_NegVal, MTurk_F1_PosVal", "MTurk_F1_PosVal, MTurk_F2_Negval", "MTurk_F2_Negval, SMU_F2_PhysPosVal", "SMU_F2_PhysPosVal, SMU_F3_BroadNegVal")))

twoFL_split_PN <- twoFL_df_PN[twoFL_split_PN, ]

twoFL_split_NoNum_PN <- twoFL_split_PN[,-c(1, 10)] # removing non-numerical columns

twoFL_split_PN$firstloading <- apply(twoFL_split_NoNum_PN, 1, function(z) na.omit(z)[1]) # extract first loading 

twoFL_split_PN$firstloading <- as.numeric(twoFL_split_PN$firstloading)

twoFL_split_PN$secondloading <- apply(twoFL_split_NoNum_PN, 1, function(z) na.omit(z)[2]) # extract second loading 

twoFL_split_PN$secondloading <- as.numeric(twoFL_split_PN$secondloading)

twoFL_split_PN$firstFL_inrange <- ifelse(abs(twoFL_split_PN$firstloading) >= .40 & abs(twoFL_split_PN$firstloading) < .75, TRUE, FALSE)

twoFL_split_PN$secondFL_inrange <- ifelse(abs(twoFL_split_PN$secondloading) >= .40 & abs(twoFL_split_PN$secondloading) < .75, TRUE, FALSE)

# none true-true, so no red

twoFL_split_items_PN <- twoFL_split_PN$Item_No 

# ========================================================================= ORANGE 3 END

### THREE FACTOR LOADINGS 

threeFL_PN <- which(FL_count_PN == 3) # subsetting for items that loaded on three factors

threeFL_df_PN <- Combined_Overall_PN[threeFL_PN, ]

tbl3 <- as.data.frame(table(threeFL_df_PN$LoadedFactor))

knitr::kable(tbl3)
```

```{r}
threeFL_notsplit_PN <- with(threeFL_df_PN, which(LoadedFactor %in% c("Com_F1_PosVal, Com_F2_BroadPos, SMU_F1_CogPosVal", "Com_F1_PosVal, MTurk_F1_PosVal, SMU_F1_CogPosVal", "Com_F1_PosVal, MTurk_F1_PosVal, SMU_F2_PhysPosVal", "Com_F2_BroadPos, MTurk_F1_PosVal, SMU_F1_CogPosVal", "Com_F2_BroadPos, MTurk_F1_PosVal, SMU_F2_PhysPosVal", "Com_F3_NegVal, MTurk_F2_Negval, SMU_F3_BroadNegVal")))

threeFL_notsplit_PN <- threeFL_df_PN[threeFL_notsplit_PN, ]

threeFL_notsplit_NoNum_PN <- threeFL_notsplit_PN[,-c(1, 10)] # removing non-numerical columns

threeFL_notsplit_PN$firstloading <- apply(threeFL_notsplit_NoNum_PN, 1, function(z) na.omit(z)[1]) # extract first loading 

threeFL_notsplit_PN$firstloading <- as.numeric(threeFL_notsplit_PN$firstloading)

threeFL_notsplit_PN$secondloading <- apply(threeFL_notsplit_NoNum_PN, 1, function(z) na.omit(z)[2]) # extract second loading 

threeFL_notsplit_PN$secondloading <- as.numeric(threeFL_notsplit_PN$secondloading)

threeFL_notsplit_PN$thirdloading <- apply(threeFL_notsplit_NoNum_PN, 1, function(z) na.omit(z)[3]) # extract third loading 

threeFL_notsplit_PN$thirdloading <- as.numeric(threeFL_notsplit_PN$thirdloading)

threeFL_notsplit_PN$firstFL_inrange <- ifelse(abs(threeFL_notsplit_PN$firstloading) >= .40 & abs(threeFL_notsplit_PN$firstloading) < .75, TRUE, FALSE)

threeFL_notsplit_PN$secondFL_inrange <- ifelse(abs(threeFL_notsplit_PN$secondloading) >= .40 & abs(threeFL_notsplit_PN$secondloading) < .75, TRUE, FALSE)

threeFL_notsplit_PN$thirdFL_inrange <- ifelse(abs(threeFL_notsplit_PN$thirdloading) >= .40 & abs(threeFL_notsplit_PN$thirdloading) < .75, TRUE, FALSE)

threeFL_notsplit_PN$category <- ifelse(threeFL_notsplit_PN$firstFL_inrange == TRUE & threeFL_notsplit_PN$secondFL_inrange == TRUE & threeFL_notsplit_PN$thirdFL_inrange == TRUE, "GREEN", "NOT_GREEN")

# items that loaded in range across samples (all pos or all neg) ============= GREEN 1 START

threeFL_GREEN_PN <- with(threeFL_notsplit_PN, which(category %in% "GREEN"))

threeFL_GREEN_PN <- threeFL_notsplit_PN[threeFL_GREEN_PN, ]

threeFL_GREEN_items_PN <- threeFL_GREEN_PN$Item_No # all com, mturk, smu, no cross-loadings, so all green

# ========================================================================= GREEN 1 END 

threeFL_NOTGREEN_PN <- with(threeFL_notsplit_PN, which(category %in% "NOT_GREEN"))

threeFL_NOTGREEN_PN <- threeFL_notsplit_PN[threeFL_NOTGREEN_PN, ]

threeFL_NOTGREEN_PN$category2 <- ifelse(threeFL_NOTGREEN_PN$firstFL_inrange == FALSE & threeFL_NOTGREEN_PN$secondFL_inrange == FALSE & threeFL_NOTGREEN_PN$thirdFL_inrange == FALSE, "ORANGE", "YELLOW")

# ========================================================================= YELLOW 3 START 

threeFL_YELLOW_PN <- with(threeFL_NOTGREEN_PN, which(category2 %in% "YELLOW"))

threeFL_YELLOW_PN <- threeFL_NOTGREEN_PN[threeFL_YELLOW_PN, ]

threeFL_YELLOW_items_PN <- threeFL_YELLOW_PN$Item_No  

# ========================================================================= YELLOW 3 END 

# ========================================================================= ORANGE 4 START 

threeFL_ORANGE_PN <- with(threeFL_NOTGREEN_PN, which(category2 %in% "ORANGE"))

threeFL_ORANGE_PN <- threeFL_NOTGREEN_PN[threeFL_ORANGE_PN, ]

threeFL_ORANGE_items_PN <- threeFL_ORANGE_PN$Item_No  

# ========================================================================= ORANGE 4 END 

# orange list, items that split within or across samples but none pos & neg in range, no red == ORANGE 5 START 

threeFL_split_PN <- with(threeFL_df_PN, which(LoadedFactor %in% c("Com_F1_PosVal, Com_F3_NegVal, MTurk_F2_Negval", "Com_F1_PosVal, Com_F3_NegVal, SMU_F1_CogPosVal", "Com_F1_PosVal, MTurk_F2_Negval, SMU_F1_CogPosVal", "Com_F1_PosVal, MTurk_F2_Negval, SMU_F3_BroadNegVal", "Com_F1_PosVal, SMU_F1_CogPosVal, SMU_F3_BroadNegVal", "Com_F2_BroadPos, Com_F3_NegVal, MTurk_F1_PosVal", "Com_F2_BroadPos, MTurk_F1_PosVal, MTurk_F2_Negval", "Com_F2_BroadPos, MTurk_F2_Negval, SMU_F3_BroadNegVal", "Com_F3_NegVal, MTurk_F1_PosVal, MTurk_F2_Negval", "MTurk_F1_PosVal, MTurk_F2_Negval, SMU_F3_BroadNegVal", "MTurk_F2_Negval, SMU_F2_PhysPosVal, SMU_F3_BroadNegVal")))

threeFL_split_PN <- threeFL_df_PN[threeFL_split_PN, ]

threeFL_split_NoNum_PN <- threeFL_split_PN[,-c(1, 10)] # removing non-numerical columns

threeFL_split_PN$firstloading <- apply(threeFL_split_NoNum_PN, 1, function(z) na.omit(z)[1]) # extract first loading 

threeFL_split_PN$firstloading <- as.numeric(threeFL_split_PN$firstloading)

threeFL_split_PN$secondloading <- apply(threeFL_split_NoNum_PN, 1, function(z) na.omit(z)[2]) # extract second loading 

threeFL_split_PN$secondloading <- as.numeric(threeFL_split_PN$secondloading)

threeFL_split_PN$thirdloading <- apply(threeFL_split_NoNum_PN, 1, function(z) na.omit(z)[3]) # extract third loading 

threeFL_split_PN$thirdloading <- as.numeric(threeFL_split_PN$thirdloading)

threeFL_split_PN$firstFL_inrange <- ifelse(abs(threeFL_split_PN$firstloading) >= .40 & abs(threeFL_split_PN$firstloading) < .75, TRUE, FALSE)

threeFL_split_PN$secondFL_inrange <- ifelse(abs(threeFL_split_PN$secondloading) >= .40 & abs(threeFL_split_PN$secondloading) < .75, TRUE, FALSE)

threeFL_split_PN$thirdFL_inrange <- ifelse(abs(threeFL_split_PN$thirdloading) >= .40 & abs(threeFL_split_PN$thirdloading) < .75, TRUE, FALSE)

threeFL_split_items_PN <- threeFL_split_PN$Item_No

# ========================================================================= ORANGE 5 END 

### FOUR FACTOR LOADINGS 

fourFL_PN <- which(FL_count_PN == 4) # subsetting for items that loaded on four factors

fourFL_df_PN <- Combined_Overall_PN[fourFL_PN, ]

tbl4 <- as.data.frame(table(fourFL_df_PN$LoadedFactor))

knitr::kable(tbl4)
```

```{r}
fourFL_notsplit_PN <- with(fourFL_df_PN, which(LoadedFactor %in% c("Com_F1_PosVal, Com_F2_BroadPos, MTurk_F1_PosVal, SMU_F1_CogPosVal", "Com_F1_PosVal, Com_F2_BroadPos, MTurk_F1_PosVal, SMU_F2_PhysPosVal", "Com_F1_PosVal, Com_F2_BroadPos, SMU_F1_CogPosVal, SMU_F2_PhysPosVal", "Com_F1_PosVal, MTurk_F1_PosVal, SMU_F1_CogPosVal, SMU_F2_PhysPosVal", "Com_F2_BroadPos, MTurk_F1_PosVal, SMU_F1_CogPosVal, SMU_F2_PhysPosVal")))

fourFL_notsplit_PN <- fourFL_df_PN[fourFL_notsplit_PN, ]

fourFL_notsplit_NoNum_PN <- fourFL_notsplit_PN[,-c(1, 10)] # removing non-numerical columns

fourFL_notsplit_PN$firstloading <- apply(fourFL_notsplit_NoNum_PN, 1, function(z) na.omit(z)[1]) # extract first loading 

fourFL_notsplit_PN$firstloading <- as.numeric(fourFL_notsplit_PN$firstloading)

fourFL_notsplit_PN$secondloading <- apply(fourFL_notsplit_NoNum_PN, 1, function(z) na.omit(z)[2]) # extract second loading 

fourFL_notsplit_PN$secondloading <- as.numeric(fourFL_notsplit_PN$secondloading)

fourFL_notsplit_PN$thirdloading <- apply(fourFL_notsplit_NoNum_PN, 1, function(z) na.omit(z)[3]) # extract third loading

fourFL_notsplit_PN$thirdloading <- as.numeric(fourFL_notsplit_PN$thirdloading)

fourFL_notsplit_PN$fourthloading <- apply(fourFL_notsplit_NoNum_PN, 1, function(z) na.omit(z)[4]) # extract fourth loading

fourFL_notsplit_PN$fourthloading <- as.numeric(fourFL_notsplit_PN$fourthloading)

fourFL_notsplit_PN$firstFL_inrange <- ifelse(abs(fourFL_notsplit_PN$firstloading) >= .40 & abs(fourFL_notsplit_PN$firstloading) < .75, TRUE, FALSE)

fourFL_notsplit_PN$secondFL_inrange <- ifelse(abs(fourFL_notsplit_PN$secondloading) >= .40 & abs(fourFL_notsplit_PN$secondloading) < .75, TRUE, FALSE)

fourFL_notsplit_PN$thirdFL_inrange<- ifelse(abs(fourFL_notsplit_PN$thirdloading) >= .40 & abs(fourFL_notsplit_PN$thirdloading) < .75, TRUE, FALSE)

fourFL_notsplit_PN$fourthFL_inrange <- ifelse(abs(fourFL_notsplit_PN$fourthloading) >= .40 & abs(fourFL_notsplit_PN$fourthloading) < .75, TRUE, FALSE)

fourFL_notsplit_loadings_PN <- fourFL_notsplit_PN[,10:18]
```

```{r}
tbl_row1 <- as.data.frame(fourFL_notsplit_loadings_PN[1,])

knitr::kable(tbl_row1) # yellow, good in two out of three samples 
```

```{r}
tbl_row2 <- as.data.frame(fourFL_notsplit_loadings_PN[2,])

knitr::kable(tbl_row2) # orange, loaded pos and in range across all three but loaded on two in com, not <.30 in one of the two
```

```{r}
tbl_row3 <- as.data.frame(fourFL_notsplit_loadings_PN[3,])

knitr::kable(tbl_row3) # orange, did not load in range on any factor
```

```{r}
tbl_row4 <- as.data.frame(fourFL_notsplit_loadings_PN[4,])

knitr::kable(tbl_row4) # yellow, only in range in two of three samples
```

```{r}
tbl_row5 <- as.data.frame(fourFL_notsplit_loadings_PN[5,])

knitr::kable(tbl_row5) # green, in range in all samples, cross-loading for smu sample <.30 
```

```{r}
tbl_row6 <- as.data.frame(fourFL_notsplit_loadings_PN[6,])

knitr::kable(tbl_row6) # yellow, only in range in two of three samples
```

```{r}
tbl_row7 <- as.data.frame(fourFL_notsplit_loadings_PN[7,])

knitr::kable(tbl_row7) # yellow, only in range in two of three samples
```

```{r}
tbl_row8 <- as.data.frame(fourFL_notsplit_loadings_PN[8,])

knitr::kable(tbl_row8) # yellow, only in range in one of three samples
```

```{r}
tbl_row9 <- as.data.frame(fourFL_notsplit_loadings_PN[9,])

knitr::kable(tbl_row9) # yellow, only in range in one of three samples
```

```{r}
tbl_row10 <- as.data.frame(fourFL_notsplit_loadings_PN[10,])

knitr::kable(tbl_row10) # yellow, only in range in two of three samples
```

```{r}
tbl_row11 <- as.data.frame(fourFL_notsplit_loadings_PN[11,])

knitr::kable(tbl_row11) # yellow, only in range in one of three samples
```

```{r}
tbl_row12 <- as.data.frame(fourFL_notsplit_loadings_PN[12,])

knitr::kable(tbl_row12) # yellow, only in range in one of three samples
```

```{r}
tbl_row13 <- as.data.frame(fourFL_notsplit_loadings_PN[13,])

knitr::kable(tbl_row13) # yellow, only in range in one of three samples
```

```{r}
tbl_row14 <- as.data.frame(fourFL_notsplit_loadings_PN[14,])

knitr::kable(tbl_row14) # orange, in range for only com and smu and had cross-loading >.30 in smu
```

```{r}
tbl_row15 <- as.data.frame(fourFL_notsplit_loadings_PN[15,])

knitr::kable(tbl_row15) # orange, did not load in range on any factor
```

```{r}
tbl_row16 <- as.data.frame(fourFL_notsplit_loadings_PN[16,])

knitr::kable(tbl_row16) # yellow, only in range on two of three samples
```

```{r}
tbl_row17 <- as.data.frame(fourFL_notsplit_loadings_PN[17,])

knitr::kable(tbl_row17) # green, in range in all samples, cross-loading for smu sample <.30 
```

```{r}
tbl_row18 <- as.data.frame(fourFL_notsplit_loadings_PN[18,])

knitr::kable(tbl_row18) # yellow, only in range on two of three samples
```

```{r}
tbl_row19 <- as.data.frame(fourFL_notsplit_loadings_PN[19,])

knitr::kable(tbl_row19) # yellow, only in range on two of three samples
```

```{r}
tbl_row20 <- as.data.frame(fourFL_notsplit_loadings_PN[20,])

knitr::kable(tbl_row20) # yellow, only in range on two of three samples
```

```{r}
# non-split items that were green as indicated above ======================== GREEN 2 START 

fourFL_GREEN_PN <- fourFL_notsplit_PN[c(5, 17),]

fourFL_GREEN_items_PN <- fourFL_GREEN_PN$Item_No

# =========================================================================== GREEN 2 END 

# non-split items that were yellow as indicated above ======================== YELLOW 4 START 

fourFL_YELLOW_PN <- fourFL_notsplit_PN[-c(2, 3, 5, 14, 15, 17),]

fourFL_YELLOW_items_PN <- fourFL_YELLOW_PN$Item_No

# =========================================================================== YELLOW 4 END 

# non-split items that were orange as indicated above ======================== ORANGE 6 START 

fourFL_ORANGE_PN <- fourFL_notsplit_PN[c(2, 3, 14, 15),]

fourFL_ORANGE_items_PN <- fourFL_ORANGE_PN$Item_No

# =========================================================================== ORANGE 6 END 
```

```{r}
fourFL_split_PN <- with(fourFL_df_PN, which(LoadedFactor %in% c("Com_F2_BroadPos, Com_F3_NegVal, MTurk_F1_PosVal, MTurk_F2_Negval", "Com_F2_BroadPos, Com_F3_NegVal, MTurk_F1_PosVal, SMU_F2_PhysPosVal", "Com_F2_BroadPos, Com_F3_NegVal, MTurk_F2_Negval, SMU_F3_BroadNegVal", "Com_F2_BroadPos, MTurk_F2_Negval, SMU_F1_CogPosVal, SMU_F2_PhysPosVal", "Com_F2_BroadPos, MTurk_F2_Negval, SMU_F2_PhysPosVal, SMU_F3_BroadNegVal", "Com_F3_NegVal, MTurk_F1_PosVal, MTurk_F2_Negval, SMU_F2_PhysPosVal", "Com_F3_NegVal, MTurk_F1_PosVal, MTurk_F2_Negval, SMU_F3_BroadNegVal", "Com_F3_NegVal, MTurk_F2_Negval, SMU_F1_CogPosVal, SMU_F3_BroadNegVal", "MTurk_F1_PosVal, MTurk_F2_Negval, SMU_F2_PhysPosVal, SMU_F3_BroadNegVal")))

fourFL_split_PN <- fourFL_df_PN[fourFL_split_PN, ]

fourFL_split_NoNum_PN <- fourFL_split_PN[,-c(1, 10)] # removing non-numerical columns

fourFL_split_PN$firstloading <- apply(fourFL_split_NoNum_PN, 1, function(z) na.omit(z)[1]) # extract first loading 

fourFL_split_PN$firstloading <- as.numeric(fourFL_split_PN$firstloading) 

fourFL_split_PN$secondloading <- apply(fourFL_split_NoNum_PN, 1, function(z) na.omit(z)[2]) # extract second loading 

fourFL_split_PN$secondloading <- as.numeric(fourFL_split_PN$secondloading)

fourFL_split_PN$thirdloading <- apply(fourFL_split_NoNum_PN, 1, function(z) na.omit(z)[3]) # extract third loading

fourFL_split_PN$thirdloading <- as.numeric(fourFL_split_PN$thirdloading)

fourFL_split_PN$fourthloading <- apply(fourFL_split_NoNum_PN, 1, function(z) na.omit(z)[4]) # extract fourth loading

fourFL_split_PN$fourthloading <- as.numeric(fourFL_split_PN$fourthloading)

fourFL_split_PN$firstFL_inrange <- ifelse(abs(fourFL_split_PN$firstloading) >= .40 & abs(fourFL_split_PN$firstloading) < .75, TRUE, FALSE)

fourFL_split_PN$secondFL_inrange <- ifelse(abs(fourFL_split_PN$secondloading) >= .40 & abs(fourFL_split_PN$secondloading) < .75, TRUE, FALSE)

fourFL_split_PN$thirdFL_inrange<- ifelse(abs(fourFL_split_PN$thirdloading) >= .40 & abs(fourFL_split_PN$thirdloading) < .75, TRUE, FALSE)

fourFL_split_PN$fourthFL_inrange <- ifelse(abs(fourFL_split_PN$fourthloading) >= .40 & abs(fourFL_split_PN$fourthloading) < .75, TRUE, FALSE)

fourFL_split_loadings_PN <- fourFL_split_PN[,10:18]
```

```{r}
split_tbl_row1 <- as.data.frame(fourFL_split_loadings_PN[1,])

knitr::kable(split_tbl_row1) # orange
```

```{r}
split_tbl_row2 <- as.data.frame(fourFL_split_loadings_PN[2,])

knitr::kable(split_tbl_row2) # orange
```

```{r}
split_tbl_row3 <- as.data.frame(fourFL_split_loadings_PN[3,])

knitr::kable(split_tbl_row3) # red
```

```{r}
split_tbl_row4 <- as.data.frame(fourFL_split_loadings_PN[4,])

knitr::kable(split_tbl_row4) # orange
```

```{r}
split_tbl_row5 <- as.data.frame(fourFL_split_loadings_PN[5,])

knitr::kable(split_tbl_row5) # orange
```

```{r}
split_tbl_row6 <- as.data.frame(fourFL_split_loadings_PN[6,])

knitr::kable(split_tbl_row6) # orange
```

```{r}
split_tbl_row7 <- as.data.frame(fourFL_split_loadings_PN[7,])

knitr::kable(split_tbl_row7) # orange
```

```{r}
split_tbl_row8 <- as.data.frame(fourFL_split_loadings_PN[8,])

knitr::kable(split_tbl_row8) # orange
```

```{r}
split_tbl_row9 <- as.data.frame(fourFL_split_loadings_PN[9,])

knitr::kable(split_tbl_row9) # orange
```

```{r}
split_tbl_row10 <- as.data.frame(fourFL_split_loadings_PN[10,])

knitr::kable(split_tbl_row10) # orange
```

```{r}
split_tbl_row11 <- as.data.frame(fourFL_split_loadings_PN[11,])

knitr::kable(split_tbl_row11) # orange
```

```{r}
split_tbl_row12 <- as.data.frame(fourFL_split_loadings_PN[12,])

knitr::kable(split_tbl_row12) # red
```

```{r}
split_tbl_row13 <- as.data.frame(fourFL_split_loadings_PN[13,])

knitr::kable(split_tbl_row13) # orange
```

```{r}
split_tbl_row14 <- as.data.frame(fourFL_split_loadings_PN[14,])

knitr::kable(split_tbl_row14) # red
```

```{r}
split_tbl_row15 <- as.data.frame(fourFL_split_loadings_PN[15,])

knitr::kable(split_tbl_row15) # orange
```

```{r}
split_tbl_row16 <- as.data.frame(fourFL_split_loadings_PN[16,])

knitr::kable(split_tbl_row16) # orange
```

```{r}
split_tbl_row17 <- as.data.frame(fourFL_split_loadings_PN[17,])

knitr::kable(split_tbl_row17) # orange
```

```{r}
split_tbl_row18 <- as.data.frame(fourFL_split_loadings_PN[18,])

knitr::kable(split_tbl_row18) # orange
```

```{r}
# split items that were orange as indicated above =========================== ORANGE 7 START 

fourFL_split_ORANGE_PN <- fourFL_split_PN[-c(3, 12, 14),]

fourFL_split_ORANGE_items_PN <- fourFL_split_ORANGE_PN$Item_No

# =========================================================================== ORANGE 7 END 

# split items that were red as indicated above ============================== RED 2 START 

fourFL_split_RED_PN <- fourFL_split_PN[c(3, 12, 14),]

fourFL_split_RED_items_PN <- fourFL_split_RED_PN$Item_No

# =========================================================================== RED 2 END 

### FIVE FACTOR LOADINGS 

fiveFL_PN <- which(FL_count_PN == 5) # subsetting for items that loaded on five factors

fiveFL_df_PN <- Combined_Overall_PN[fiveFL_PN, ]

tbl5 <- as.data.frame(table(fiveFL_df_PN$LoadedFactor))

knitr::kable(tbl5)
```

```{r}
fiveFL_NoNum_PN <- fiveFL_df_PN[,-c(1, 10)] # removing non-numerical columns

fiveFL_df_PN$firstloading <- apply(fiveFL_NoNum_PN, 1, function(z) na.omit(z)[1]) # extract first loading 

fiveFL_df_PN$firstloading <- as.numeric(fiveFL_df_PN$firstloading) 

fiveFL_df_PN$secondloading <- apply(fiveFL_NoNum_PN, 1, function(z) na.omit(z)[2]) # extract second loading 

fiveFL_df_PN$secondloading <- as.numeric(fiveFL_df_PN$secondloading)

fiveFL_df_PN$thirdloading <- apply(fiveFL_NoNum_PN, 1, function(z) na.omit(z)[3]) # extract third loading

fiveFL_df_PN$thirdloading <- as.numeric(fiveFL_df_PN$thirdloading)

fiveFL_df_PN$fourthloading <- apply(fiveFL_NoNum_PN, 1, function(z) na.omit(z)[4]) # extract fourth loading

fiveFL_df_PN$fourthloading <- as.numeric(fiveFL_df_PN$fourthloading)

fiveFL_df_PN$fifthloading <- apply(fiveFL_NoNum_PN, 1, function(z) na.omit(z)[5]) # extract fifth loading

fiveFL_df_PN$fifthloading <- as.numeric(fiveFL_df_PN$fifthloading)

fiveFL_df_PN$firstFL_inrange <- ifelse(abs(fiveFL_df_PN$firstloading) >= .40 & abs(fiveFL_df_PN$firstloading) < .75, TRUE, FALSE)

fiveFL_df_PN$secondFL_inrange <- ifelse(abs(fiveFL_df_PN$secondloading) >= .40 & abs(fiveFL_df_PN$secondloading) < .75, TRUE, FALSE)

fiveFL_df_PN$thirdFL_inrange<- ifelse(abs(fiveFL_df_PN$thirdloading) >= .40 & abs(fiveFL_df_PN$thirdloading) < .75, TRUE, FALSE)

fiveFL_df_PN$fourthFL_inrange <- ifelse(abs(fiveFL_df_PN$fourthloading) >= .40 & abs(fiveFL_df_PN$fourthloading) < .75, TRUE, FALSE)

fiveFL_df_PN$fifthFL_inrange <- ifelse(abs(fiveFL_df_PN$fifthloading) >= .40 & abs(fiveFL_df_PN$fifthloading) < .75, TRUE, FALSE)

fiveFL_df_loadings_PN <- fiveFL_df_PN[,10:20]
```

```{r}
fiveFL_tbl_row1 <- as.data.frame(fiveFL_df_loadings_PN[1,])

knitr::kable(fiveFL_tbl_row1) # green, loaded in range in all three samples, cross-loadings for com and smu <.30
```

```{r}
fiveFL_tbl_row2 <- as.data.frame(fiveFL_df_loadings_PN[2,])

knitr::kable(fiveFL_tbl_row2) # orange, loaded in range in all three samples but also had cross-loadings >.30 for com and smu
```

```{r}
fiveFL_tbl_row3 <- as.data.frame(fiveFL_df_loadings_PN[3,])

knitr::kable(fiveFL_tbl_row3) # yellow, in range in only two of three samples, no cross-loadings >.30
```

```{r}
fiveFL_tbl_row4 <- as.data.frame(fiveFL_df_loadings_PN[4,])

knitr::kable(fiveFL_tbl_row4) # green, loaded in range in all three samples, cross-loadings for com and smu <.30
```

```{r}
fiveFL_tbl_row5 <- as.data.frame(fiveFL_df_loadings_PN[5,])

knitr::kable(fiveFL_tbl_row5) # red, in range for both pos and neg val factors in mturk
```

```{r}
fiveFL_tbl_row6 <- as.data.frame(fiveFL_df_loadings_PN[6,])

knitr::kable(fiveFL_tbl_row6) # orange, had weak loadings across both pos and neg factors although in range for only mturk annd smu neg
```

```{r}
fiveFL_tbl_row7 <- as.data.frame(fiveFL_df_loadings_PN[7,])

knitr::kable(fiveFL_tbl_row7) # orange, had weak loadings across both pos and neg factors although in range for only com and mturk neg
```

```{r}
fiveFL_tbl_row8 <- as.data.frame(fiveFL_df_loadings_PN[8,])

knitr::kable(fiveFL_tbl_row8) # orange, had weak loadings across both pos and neg factors although in range for only smu pos
```

```{r}
fiveFL_tbl_row9 <- as.data.frame(fiveFL_df_loadings_PN[9,])

knitr::kable(fiveFL_tbl_row9) # orange, had weak loadings across both pos and neg factors although in range for only mturk pos
```

```{r}
# items that were green as indicated above ================================== GREEN 3 START

fiveFL_GREEN_PN <- fiveFL_df_PN[c(1, 4),]

fiveFL_GREEN_items_PN <- fiveFL_GREEN_PN$Item_No

# =========================================================================== GREEN 3 END

# items that were yellow as indicated above ================================= YELLOW 5 START

fiveFL_YELLOW_PN <- fiveFL_df_PN[c(3),]

fiveFL_YELLOW_items_PN <- fiveFL_YELLOW_PN$Item_No

# =========================================================================== YELLOW 5 END

# items that were orange as indicated above ================================= ORANGE 8 START 

fiveFL_ORANGE_PN <- fiveFL_df_PN[c(5),]

fiveFL_ORANGE_items_PN <- fiveFL_ORANGE_PN$Item_No

# =========================================================================== ORANGE 8 END

# items that were red as indicated above ==================================== RED 3 START 

fiveFL_RED_PN <- fiveFL_df_PN[-c(1, 3, 4, 5),]

fiveFL_RED_items_PN <- fiveFL_RED_PN$Item_No

# =========================================================================== RED 3 END

### SIX FACTOR LOADINGS 

sixFL_PN <- which(FL_count_PN == 6) # subsetting for items that loaded on six factors

sixFL_df_PN <- Combined_Overall_PN[sixFL_PN, ]

tbl6 <- as.data.frame(table(sixFL_df_PN$LoadedFactor))

knitr::kable(tbl6)
```

```{r}
sixFL_NoNum_PN <- sixFL_df_PN[,-c(1, 10)] # removing non-numerical columns

sixFL_df_PN$firstloading <- apply(sixFL_NoNum_PN, 1, function(z) na.omit(z)[1]) # extract first loading 

sixFL_df_PN$firstloading <- as.numeric(sixFL_df_PN$firstloading) 

sixFL_df_PN$secondloading <- apply(sixFL_NoNum_PN, 1, function(z) na.omit(z)[2]) # extract second loading 

sixFL_df_PN$secondloading <- as.numeric(sixFL_df_PN$secondloading)

sixFL_df_PN$thirdloading <- apply(sixFL_NoNum_PN, 1, function(z) na.omit(z)[3]) # extract third loading

sixFL_df_PN$thirdloading <- as.numeric(sixFL_df_PN$thirdloading)

sixFL_df_PN$fourthloading <- apply(sixFL_NoNum_PN, 1, function(z) na.omit(z)[4]) # extract fourth loading

sixFL_df_PN$fourthloading <- as.numeric(sixFL_df_PN$fourthloading)

sixFL_df_PN$fifthloading <- apply(sixFL_NoNum_PN, 1, function(z) na.omit(z)[5]) # extract fifth loading

sixFL_df_PN$fifthloading <- as.numeric(sixFL_df_PN$fifthloading)

sixFL_df_PN$sixthloading <- apply(sixFL_NoNum_PN, 1, function(z) na.omit(z)[6]) # extract sixth loading

sixFL_df_PN$sixthloading <- as.numeric(sixFL_df_PN$sixthloading)

sixFL_df_PN$firstFL_inrange <- ifelse(abs(sixFL_df_PN$firstloading) >= .40 & abs(sixFL_df_PN$firstloading) < .75, TRUE, FALSE)

sixFL_df_PN$secondFL_inrange <- ifelse(abs(sixFL_df_PN$secondloading) >= .40 & abs(sixFL_df_PN$secondloading) < .75, TRUE, FALSE)

sixFL_df_PN$thirdFL_inrange<- ifelse(abs(sixFL_df_PN$thirdloading) >= .40 & abs(sixFL_df_PN$thirdloading) < .75, TRUE, FALSE)

sixFL_df_PN$fourthFL_inrange <- ifelse(abs(sixFL_df_PN$fourthloading) >= .40 & abs(sixFL_df_PN$fourthloading) < .75, TRUE, FALSE)

sixFL_df_PN$fifthFL_inrange <- ifelse(abs(sixFL_df_PN$fifthloading) >= .40 & abs(sixFL_df_PN$fifthloading) < .75, TRUE, FALSE)

sixFL_df_PN$sixthFL_inrange <- ifelse(abs(sixFL_df_PN$fifthloading) >= .40 & abs(sixFL_df_PN$sixthloading) < .75, TRUE, FALSE)

sixFL_df_loadings_PN <- sixFL_df_PN[,10:22]
```

```{r}
sixFL_tbl_row1 <- as.data.frame(sixFL_df_loadings_PN[1,])

knitr::kable(sixFL_tbl_row1) # orange, had weak loadings across both pos and neg factors although in range for only com and mturk pos
```

```{r}
sixFL_tbl_row2 <- as.data.frame(sixFL_df_loadings_PN[2,])

knitr::kable(sixFL_tbl_row2) # orange, had weak loadings across both pos and neg factors although in range for only com and mturk neg
```

```{r}
# ============================================================ ORANGE 9 START 

sixFL_items_PN <- sixFL_df_PN$Item_No

# ============================================================ ORANGE 9 END
```

```{r}
red_list <- sort(c(zeroFL_PN, fourFL_split_RED_items_PN, fiveFL_RED_items_PN))

orange_list <- sort(c(oneFL_notir_items_PN, twoFL_ORANGE_items_PN, twoFL_split_items_PN, threeFL_ORANGE_items_PN, threeFL_split_items_PN, fourFL_ORANGE_items_PN, fourFL_split_ORANGE_items_PN, fiveFL_ORANGE_items_PN, sixFL_items_PN))

yellow_list <- sort(c(oneFL_inrange_items_PN, twoFL_YELLOW_items_PN, threeFL_YELLOW_items_PN, fourFL_YELLOW_items_PN, fiveFL_YELLOW_items_PN))

green_list <- sort(c(threeFL_GREEN_items_PN, fourFL_GREEN_items_PN, fiveFL_GREEN_items_PN))

```

```{r}
Combined_Overall_PN$category <- ifelse(Combined_Overall_PN$Item_No %in% red_list, 1, 
                                        ifelse(Combined_Overall_PN$Item_No %in% orange_list, 2, 
                                               ifelse(Combined_Overall_PN$Item_No %in% yellow_list, 3, 4)))

my_backgrounds <- c("red", "orange", "yellow", "lawngreen")     

spec_color2 <- function(x, alpha = 1, begin = 0, end = 1,
         direction = 1, option = "D",
         na_color = "#BBBBBB", scale_from = NULL,
         palette = viridisLite::viridis(256, alpha, begin, end, direction, option)) {
  n <- length(palette)
  if (is.null(scale_from)) {
    x <- round(scales::rescale(x, c(1, n)))
  } else {
    x <- round(scales::rescale(x, to = c(1, n),
                       from = scale_from))
  }
  
  color_code <- palette[x]
  color_code[is.na(color_code)] <- na_color
  return(color_code)
}
```

```{r}
item_list <- read_csv("itemlist.csv", col_names = FALSE)
```

```{r}
Combined_Overall_PN$Item <- item_list$X1

Combined_Overall_PN <- Combined_Overall_PN[ ,c(1, 12, 2:11)]
```

```{r}
knitr::kable(Combined_Overall_PN, booktabs = TRUE) %>%
  column_spec(1:12, color = "black", background = spec_color2(Combined_Overall_PN$category, palette = my_backgrounds)) %>%
  kable_styling(position="center") %>%
  scroll_box(height = "300px")  
```

### Analysis Excluding Red Pos/Neg Valence Factors 

```{r}
Combined_Overall_NoPN <- Combined_Overall_Sample[ ,c(1, 5:8, 11:15, 19:23)]

Combined_NoPN_NoNum <- Combined_Overall_NoPN[,-1]

Combined_Overall_NoPN$LoadedFactor <- apply(Combined_NoPN_NoNum, 1, function(i) paste(colnames(Combined_NoPN_NoNum)[!is.na(i) ], collapse = ", "))
```

```{r, results='asis'}
function2 <- function(x) {
  count.fields(textConnection(Combined_Overall_NoPN$LoadedFactor[x]), sep = ",", blank.lines.skip = FALSE)
}

tbl_NP <- as.data.frame(table(function2(1:312)))

knitr::kable(tbl_NP)
```

```{r}
FL_count_NP <- as.list(function2(1:312)) # number of factor loadings per item 

### ZERO FACTOR LOADINGS ###

# red list, items that did not load on any factor =========================== RED 1 START

zeroFL_NP <- which(FL_count_NP == 0)

# =========================================================================== RED 1 END

### ONE FACTOR LOADING ###

oneFL_NP <- which(FL_count_NP == 1) # subsetting for items that loaded on one factor only

oneFL_df_NP <- Combined_Overall_NoPN[oneFL_NP, ]

oneFL_df_NP$loadedFL <- apply(oneFL_df_NP[,-1], 1, function(z) na.omit(z)[1])

oneFL_df_NP$loadedFL <- as.numeric(oneFL_df_NP$loadedFL)

# items that loaded >=.4 & <.75 on one factor ============================== YELLOW 1 START

oneFL_inrange_NP <- which(abs(oneFL_df_NP$loadedFL)>= .40 & abs(oneFL_df_NP$loadedFL) < .75)

oneFL_inrange_NP <- oneFL_df_NP[oneFL_inrange_NP, ]

oneFL_inrange_items_NP <- oneFL_inrange_NP$Item_No 

# ========================================================================== YELLOW 1 END

# orange list, items that loaded on one factor only but with <.4 or >=.75 loading == ORANGE 1 START

oneFL_notir_NP <- which(abs(oneFL_df_NP$loadedFL) < .40 | abs(oneFL_df_NP$loadedFL) >= .75)

oneFL_notir_NP <- oneFL_df_NP[oneFL_notir_NP, ]

oneFL_notir_items_NP <- oneFL_notir_NP$Item_No

# ================================================================================== ORANGE 1 END

### TWO FACTOR LOADINGS 

twoFL_NP <- which(FL_count_NP == 2) # subsetting for items that loaded on two factors

twoFL_df_NP <- Combined_Overall_NoPN[twoFL_NP, ]

tbl2_NP <- as.data.frame(table(twoFL_df_NP$LoadedFactor))

knitr::kable(tbl2_NP)
```

```{r}
twoFL_notsplit_NP <- with(twoFL_df_NP, which(LoadedFactor %in% c("MTurk_F4_PosAtt, SMU_F6_PosAtt", "MTurk_F6_Flo, SMU_F8_Flo")))

twoFL_notsplit_NP <- twoFL_df_NP[twoFL_notsplit_NP, ]

twoFL_notsplit_NoNum_NP <- twoFL_notsplit_NP[,-c(1, 16)] # removing non-numerical columns

twoFL_notsplit_NP$firstloading <- apply(twoFL_notsplit_NoNum_NP, 1, function(z) na.omit(z)[1]) # extract first loading 

twoFL_notsplit_NP$firstloading <- as.numeric(twoFL_notsplit_NP$firstloading)

twoFL_notsplit_NP$secondloading <- apply(twoFL_notsplit_NoNum_NP, 1, function(z) na.omit(z)[2]) # extract second loading 

twoFL_notsplit_NP$secondloading <- as.numeric(twoFL_notsplit_NP$secondloading)

twoFL_notsplit_NP$firstFL_inrange <- ifelse(abs(twoFL_notsplit_NP$firstloading) >= .40 & abs(twoFL_notsplit_NP$firstloading) < .75, TRUE, FALSE)

twoFL_notsplit_NP$secondFL_inrange <- ifelse(abs(twoFL_notsplit_NP$secondloading) >= .40 & abs(twoFL_notsplit_NP$secondloading) < .75, TRUE, FALSE)

twoFL_notsplit_NP$category <- ifelse(twoFL_notsplit_NP$firstFL_inrange == TRUE & twoFL_notsplit_NP$secondFL_inrange == TRUE, "GREEN", ifelse(twoFL_notsplit_NP$firstFL_inrange == TRUE & twoFL_notsplit_NP$secondFL_inrange == FALSE, "YELLOW", ifelse(twoFL_notsplit_NP$firstFL_inrange == TRUE & twoFL_notsplit_NP$secondFL_inrange == FALSE, "YELLOW", "ORANGE")))

# ========================================================================= GREEN 1 START

twoFL_NS_GREEN_NP <- with(twoFL_notsplit_NP, which(category %in% "GREEN"))

twoFL_NS_GREEN_NP <- twoFL_notsplit_NP[twoFL_NS_GREEN_NP, ]

twoFL_NS_GREENitems_NP <- twoFL_NS_GREEN_NP$Item_No  

# ========================================================================= GREEN 1 END 

# ========================================================================= YELLOW 2 START 

twoFL_NS_YELLOW_NP <- with(twoFL_notsplit_NP, which(category %in% "YELLOW"))

twoFL_NS_YELLOW_NP <- twoFL_notsplit_NP[twoFL_NS_YELLOW_NP, ]

twoFL_NS_YELLOWitems_NP <- twoFL_NS_YELLOW_NP$Item_No  

# ========================================================================= YELLOW 2 END 

# ========================================================================= ORANGE 2 START 

twoFL_NS_ORANGE_NP <- with(twoFL_notsplit_NP, which(category %in% "ORANGE"))

twoFL_NS_ORANGE_NP <- twoFL_notsplit_NP[twoFL_NS_ORANGE_NP, ]

twoFL_NS_ORANGEitems_NP <- twoFL_NS_ORANGE_NP$Item_No  

# ========================================================================= ORANGE 2 END 

twoFL_split_NP <- with(twoFL_df_NP, which(LoadedFactor %in% c("Com_F4_NegPhys, Com_F5_Prog", "Com_F4_NegPhys, MTurk_F3_Cog", "Com_F4_NegPhys, MTurk_F5_Gar", "Com_F4_NegPhys, SMU_F4_NegAtt", "Com_F4_NegPhys, SMU_F7_CompSoc", "Com_F4_NegPhys, SMU_F8_Flo", "Com_F5_Prog, MTurk_F3_Cog", "Com_F6_PosAtt, SMU_F7_CompSoc", "Com_F7_Soc, MTurk_F3_Cog", "Com_F7_Soc, MTurk_F4_PosAtt", "Com_F7_Soc, SMU_F8_Flo", "MTurk_F3_Cog, MTurk_F4_PosAtt", "MTurk_F3_Cog, MTurk_F6_Flo", "MTurk_F3_Cog, SMU_F8_Flo", "MTurk_F4_PosAtt, SMU_F8_Flo", "MTurk_F5_Gar, SMU_F4_NegAtt", "MTurk_F5_Gar, SMU_F8_Flo", "SMU_F7_CompSoc, SMU_F8_Flo")))

twoFL_split_NP <- twoFL_df_NP[twoFL_split_NP, ]

twoFL_split_NoNum_NP <- twoFL_split_NP[,-c(1, 16)] # removing non-numerical columns

twoFL_split_NP$firstloading <- apply(twoFL_split_NoNum_NP, 1, function(z) na.omit(z)[1]) # extract first loading 

twoFL_split_NP$firstloading <- as.numeric(twoFL_split_NP$firstloading)

twoFL_split_NP$secondloading <- apply(twoFL_split_NoNum_NP, 1, function(z) na.omit(z)[2]) # extract second loading 

twoFL_split_NP$secondloading <- as.numeric(twoFL_split_NP$secondloading)

twoFL_split_NP$firstFL_inrange <- ifelse(abs(twoFL_split_NP$firstloading) >= .40 & abs(twoFL_split_NP$firstloading) < .75, TRUE, FALSE)

twoFL_split_NP$firstFL_loadingL030 <- ifelse(abs(twoFL_split_NP$firstloading) < .30, TRUE, FALSE)

twoFL_split_NP$secondFL_inrange <- ifelse(abs(twoFL_split_NP$secondloading) >= .40 & abs(twoFL_split_NP$secondloading) < .75, TRUE, FALSE)

twoFL_split_NP$secondFL_loadingL030 <- ifelse(abs(twoFL_split_NP$secondloading) < .30, TRUE, FALSE)

twoFL_split_NP$category <- ifelse(twoFL_split_NP$firstFL_inrange == TRUE & twoFL_split_NP$secondFL_inrange == FALSE & twoFL_split_NP$firstFL_loadingL030 == FALSE & twoFL_split_NP$secondFL_loadingL030 == TRUE, "YELLOW", ifelse(twoFL_split_NP$firstFL_inrange == FALSE & twoFL_split_NP$secondFL_inrange == TRUE & twoFL_split_NP$firstFL_loadingL030 == TRUE & twoFL_split_NP$secondFL_loadingL030 == FALSE, "YELLOW", ifelse( twoFL_split_NP$firstFL_inrange == TRUE & twoFL_split_NP$secondFL_inrange == TRUE, "RED", "ORANGE")))

# ========================================================================= YELLOW 3 START

twoFL_SP_YELLOW_NP <- with(twoFL_split_NP, which(category %in% "YELLOW"))

twoFL_SP_YELLOW_NP <- twoFL_split_NP[twoFL_SP_YELLOW_NP, ]

twoFL_SP_YELLOWitems_NP <- twoFL_SP_YELLOW_NP$Item_No  

# ========================================================================= YELLOW 3 END   

# ========================================================================= ORANGE 3 START

twoFL_SP_ORANGE_NP <- with(twoFL_split_NP, which(category %in% "ORANGE"))

twoFL_SP_ORANGE_NP <- twoFL_split_NP[twoFL_SP_ORANGE_NP, ]

twoFL_SP_ORANGEitems_NP <- twoFL_SP_ORANGE_NP$Item_No  

# ========================================================================= ORANGE 3 END 

# ========================================================================= RED 2 START

twoFL_SP_RED_NP <- with(twoFL_split_NP, which(category %in% "RED"))

twoFL_SP_RED_NP <- twoFL_split_NP[twoFL_SP_RED_NP, ]

twoFL_SP_REDitems_NP <- twoFL_SP_RED_NP$Item_No  

# ========================================================================= RED 2 END 

### THREEE FACTOR LOADINGS 

threeFL_NP <- which(FL_count_NP == 3) # subsetting for items that loaded on three factors

threeFL_df_NP <- Combined_Overall_NoPN[threeFL_NP, ]

tbl3_NP <- as.data.frame(table(threeFL_df_NP$LoadedFactor))

knitr::kable(tbl3_NP)
```

```{r}
threeFL_NoNum_NP <- threeFL_df_NP[,-c(1, 16)] # removing non-numerical columns

threeFL_df_NP$firstloading <- apply(threeFL_NoNum_NP, 1, function(z) na.omit(z)[1]) # extract first loading 

threeFL_df_NP$firstloading <- as.numeric(threeFL_df_NP$firstloading) 

threeFL_df_NP$secondloading <- apply(threeFL_NoNum_NP, 1, function(z) na.omit(z)[2]) # extract second loading 

threeFL_df_NP$secondloading <- as.numeric(threeFL_df_NP$secondloading)

threeFL_df_NP$thirdloading <- apply(threeFL_NoNum_NP, 1, function(z) na.omit(z)[3]) # extract third loading

threeFL_df_NP$thirdloading <- as.numeric(threeFL_df_NP$thirdloading)

threeFL_df_NP$firstFL_inrange <- ifelse(abs(threeFL_df_NP$firstloading) >= .40 & abs(threeFL_df_NP$firstloading) < .75, TRUE, FALSE)

threeFL_df_NP$secondFL_inrange <- ifelse(abs(threeFL_df_NP$secondloading) >= .40 & abs(threeFL_df_NP$secondloading) < .75, TRUE, FALSE)

threeFL_df_NP$thirdFL_inrange<- ifelse(abs(threeFL_df_NP$thirdloading) >= .40 & abs(threeFL_df_NP$thirdloading) < .75, TRUE, FALSE)

threeFL_df_loadings_NP <- threeFL_df_NP[,16:22]
```

```{r}
threeFL_tbl_row1_NP <- as.data.frame(threeFL_df_loadings_NP[1,])

knitr::kable(threeFL_tbl_row1_NP) # red, indicator for different subscales in different samples & in range 
```

```{r}
threeFL_tbl_row2_NP <- as.data.frame(threeFL_df_loadings_NP[2,])

knitr::kable(threeFL_tbl_row2_NP) # red, indicator for different subscales in different samples & in range 
```

```{r}
threeFL_tbl_row3_NP <- as.data.frame(threeFL_df_loadings_NP[3,])

knitr::kable(threeFL_tbl_row3_NP) # orange, indicator for different subscales in different samples but not in range 
```

```{r}
threeFL_tbl_row4_NP <- as.data.frame(threeFL_df_loadings_NP[4,])

knitr::kable(threeFL_tbl_row4_NP) # yellow, high FL (but >.75) for the same factor across samples
```

```{r}
threeFL_tbl_row5_NP <- as.data.frame(threeFL_df_loadings_NP[5,])

knitr::kable(threeFL_tbl_row5_NP) # green, FL in range for the same factor across samples 
```

```{r}
threeFL_tbl_row6_NP <- as.data.frame(threeFL_df_loadings_NP[6,])

knitr::kable(threeFL_tbl_row6_NP) # orange, loaded in different factors across samples but not all in range 
```
 
```{r}
threeFL_tbl_row7_NP <- as.data.frame(threeFL_df_loadings_NP[7,])

knitr::kable(threeFL_tbl_row7_NP) # green, FL in range for the same factor across samples 
```

```{r}
threeFL_tbl_row8_NP <- as.data.frame(threeFL_df_loadings_NP[8,])

knitr::kable(threeFL_tbl_row8_NP) # yellow, FL in range for the same factor across mturk and smu subscale but also .333 cross-loading for different factor in com sample 
```

```{r}
threeFL_tbl_row9_NP <- as.data.frame(threeFL_df_loadings_NP[9,])

knitr::kable(threeFL_tbl_row9_NP) # orange, weak loadings for different factors across samples 
```

```{r}
threeFL_tbl_row10_NP <- as.data.frame(threeFL_df_loadings_NP[10,])

knitr::kable(threeFL_tbl_row10_NP) # orange, weak loadings for different factors across samples 
```

```{r}
threeFL_tbl_row11_NP <- as.data.frame(threeFL_df_loadings_NP[11,])

knitr::kable(threeFL_tbl_row11_NP) # yellow, FL in range for one factor in mturk sample, cross-loadings for other factors <.30 in other samples
```

```{r}
threeFL_tbl_row12_NP <- as.data.frame(threeFL_df_loadings_NP[12,])

knitr::kable(threeFL_tbl_row12_NP) # red, indicator for different subscales in different samples & in range 
```

```{r}
threeFL_tbl_row13_NP <- as.data.frame(threeFL_df_loadings_NP[13,])

knitr::kable(threeFL_tbl_row13_NP) # yellow, indicator for same factor across different samples and in range (but with one FL >.75)
```

```{r}
threeFL_tbl_row14_NP <- as.data.frame(threeFL_df_loadings_NP[14,])

knitr::kable(threeFL_tbl_row14_NP) # green, FL in range for the same factor across samples 
```

```{r}
threeFL_tbl_row15_NP <- as.data.frame(threeFL_df_loadings_NP[15,])

knitr::kable(threeFL_tbl_row15_NP) # green, FL in range for the same factor across samples 
```

```{r}
threeFL_tbl_row16_NP <- as.data.frame(threeFL_df_loadings_NP[16,])

knitr::kable(threeFL_tbl_row16_NP) # green, FL in range for the same factor across samples 
```

```{r}
threeFL_tbl_row17_NP <- as.data.frame(threeFL_df_loadings_NP[17,])

knitr::kable(threeFL_tbl_row17_NP) # green, FL in range for the same factor across samples 
```

```{r}
threeFL_tbl_row18_NP <- as.data.frame(threeFL_df_loadings_NP[18,])

knitr::kable(threeFL_tbl_row18_NP) # yellow, indicator for same factor across different samples and in range (but with one FL < .40)
```

```{r}
threeFL_tbl_row19_NP <- as.data.frame(threeFL_df_loadings_NP[19,])

knitr::kable(threeFL_tbl_row19_NP) # yellow, FL in range for the same factor across mturk and smu subscale but also .256 cross-loading for different factor in com sample 
```

```{r}
threeFL_tbl_row20_NP <- as.data.frame(threeFL_df_loadings_NP[20,])

knitr::kable(threeFL_tbl_row20_NP) # yellow, indicator for same factor across different samples and in range (but with one FL < .40)
```

```{r}
threeFL_tbl_row21_NP <- as.data.frame(threeFL_df_loadings_NP[21,])

knitr::kable(threeFL_tbl_row21_NP) # orange, weak loadings for different factors across samples
```

```{r}
threeFL_tbl_row22_NP <- as.data.frame(threeFL_df_loadings_NP[22,])

knitr::kable(threeFL_tbl_row22_NP) # green, FL in range for the same factor across samples 
```

```{r}
threeFL_tbl_row23_NP <- as.data.frame(threeFL_df_loadings_NP[23,])

knitr::kable(threeFL_tbl_row23_NP) # green, FL in range for the same factor across samples 
```

```{r}
threeFL_tbl_row24_NP <- as.data.frame(threeFL_df_loadings_NP[24,])

knitr::kable(threeFL_tbl_row24_NP) # green, FL in range for the same factor across samples 
```

```{r}
threeFL_tbl_row25_NP <- as.data.frame(threeFL_df_loadings_NP[25,])

knitr::kable(threeFL_tbl_row25_NP) # red, indicator for different subscales in different samples & in range 
```

```{r}
threeFL_tbl_row26_NP <- as.data.frame(threeFL_df_loadings_NP[26,])

knitr::kable(threeFL_tbl_row26_NP) # red, indicator for different subscales in different samples & in range 
```

```{r}
threeFL_tbl_row27_NP <- as.data.frame(threeFL_df_loadings_NP[27,])

knitr::kable(threeFL_tbl_row27_NP) # green, FL in range for the same factor across samples 
```

```{r}
threeFL_tbl_row28_NP <- as.data.frame(threeFL_df_loadings_NP[28,])

knitr::kable(threeFL_tbl_row28_NP) # green, FL in range for the same factor across samples 
```

```{r}
threeFL_tbl_row29_NP <- as.data.frame(threeFL_df_loadings_NP[29,])

knitr::kable(threeFL_tbl_row29_NP) # red, indicator for different subscales in different samples & in range 
```

```{r}
threeFL_tbl_row30_NP <- as.data.frame(threeFL_df_loadings_NP[30,])

knitr::kable(threeFL_tbl_row30_NP) # orange, weak loadings for different factors across samples
```

```{r}
threeFL_tbl_row31_NP <- as.data.frame(threeFL_df_loadings_NP[31,])

knitr::kable(threeFL_tbl_row31_NP) # orange, loaded in different factors across samples but not all in range 
```

```{r}
threeFL_tbl_row32_NP <- as.data.frame(threeFL_df_loadings_NP[32,])

knitr::kable(threeFL_tbl_row32_NP) # yellow, indicator for same factor across different samples and in range (but with two FLs < .40)
```

```{r}
threeFL_tbl_row33_NP <- as.data.frame(threeFL_df_loadings_NP[33,])

knitr::kable(threeFL_tbl_row33_NP) # green, FL in range for the same factor across samples 
```

```{r}
threeFL_tbl_row34_NP <- as.data.frame(threeFL_df_loadings_NP[34,])

knitr::kable(threeFL_tbl_row34_NP) # green, FL in range for the same factor across samples 
```

```{r}
threeFL_tbl_row35_NP <- as.data.frame(threeFL_df_loadings_NP[35,])

knitr::kable(threeFL_tbl_row35_NP) # yellow, FL in range for the same factor across mturk and smu subscale but also .252 cross-loading for different factor in com sample 
```

```{r}
threeFL_tbl_row36_NP <- as.data.frame(threeFL_df_loadings_NP[36,])

knitr::kable(threeFL_tbl_row36_NP) # orange, weak loadings for different factors across samples
```

```{r}
threeFL_tbl_row37_NP <- as.data.frame(threeFL_df_loadings_NP[37,])

knitr::kable(threeFL_tbl_row37_NP) # red, indicator for different subscales in different samples & in range 
```

```{r}
threeFL_tbl_row38_NP <- as.data.frame(threeFL_df_loadings_NP[38,])

knitr::kable(threeFL_tbl_row38_NP) # yellow, indicator for same factor across different samples and in range (but with two FLs < .40)
```

```{r}
threeFL_tbl_row39_NP <- as.data.frame(threeFL_df_loadings_NP[39,])

knitr::kable(threeFL_tbl_row39_NP) # green, FL in range for the same factor across samples 
```

```{r}
threeFL_tbl_row40_NP <- as.data.frame(threeFL_df_loadings_NP[40,])

knitr::kable(threeFL_tbl_row40_NP) # orange, weak loadings for different factors across samples
```

```{r}
threeFL_tbl_row41_NP <- as.data.frame(threeFL_df_loadings_NP[41,])

knitr::kable(threeFL_tbl_row41_NP) # orange, weak loadings for different factors across samples
```

```{r}
threeFL_tbl_row42_NP <- as.data.frame(threeFL_df_loadings_NP[42,])

knitr::kable(threeFL_tbl_row42_NP) # yellow, indicator for same factor across different samples and in range (but with one FL < .40)
```

```{r}
threeFL_tbl_row43_NP <- as.data.frame(threeFL_df_loadings_NP[43,])

knitr::kable(threeFL_tbl_row43_NP) # orange, weak loadings for different factors across samples
```

```{r}
threeFL_tbl_row44_NP <- as.data.frame(threeFL_df_loadings_NP[44,])

knitr::kable(threeFL_tbl_row44_NP) # green, FL in range for the same factor across samples 
```

```{r}
threeFL_tbl_row45_NP <- as.data.frame(threeFL_df_loadings_NP[45,])

knitr::kable(threeFL_tbl_row45_NP) # yellow, indicator for same factor across different samples and in range (but with one FL < .40)
```

```{r}
threeFL_tbl_row46_NP <- as.data.frame(threeFL_df_loadings_NP[46,])

knitr::kable(threeFL_tbl_row46_NP) # green, FL in range for the same factor across samples 
```

```{r}
threeFL_tbl_row47_NP <- as.data.frame(threeFL_df_loadings_NP[47,])

knitr::kable(threeFL_tbl_row47_NP) # orange, weak loadings for different factors across samples
```

```{r}
threeFL_tbl_row48_NP <- as.data.frame(threeFL_df_loadings_NP[48,])

knitr::kable(threeFL_tbl_row48_NP) # orange, weak loadings for different factors across samples
```

```{r}
# =========================================================================== GREEN 3 START 

threeFL_GREEN_NP <- threeFL_df_NP[c(5, 7, 14, 15, 16, 17, 22, 23, 24, 27, 28, 33, 34, 39, 44, 46),]

threeFL_GREENitems_NP <- threeFL_GREEN_NP$Item_No

# =========================================================================== GREEN 3 END 

# =========================================================================== YELLOW 4 START 

threeFL_YELLOW_NP <- threeFL_df_NP[c(4, 8, 11, 13, 18, 19, 20, 32, 35, 38, 42, 45),]

threeFL_YELLOWitems_NP <- threeFL_YELLOW_NP$Item_No

# =========================================================================== YELLOW 4 END 

# =========================================================================== ORANGE 4 START 

threeFL_ORANGE_NP <- threeFL_df_NP[c(3, 6, 9, 10, 20, 21, 30, 31, 36, 40, 41, 43, 47, 48),]

threeFL_ORANGEitems_NP <- threeFL_ORANGE_NP$Item_No

# =========================================================================== ORANGE 4 END 

# =========================================================================== RED 3 START 

threeFL_RED_NP <- threeFL_df_NP[c(1, 2, 12, 25, 26, 29, 37),]

threeFL_REDitems_NP <- threeFL_RED_NP$Item_No

# =========================================================================== RED 3 END 

### FOUR FACTOR LOADINGS 

fourFL_NP <- which(FL_count_NP == 4) # subsetting for items that loaded on four factors

fourFL_df_NP <- Combined_Overall_NoPN[fourFL_NP, ]

tbl4_NP <- as.data.frame(table(fourFL_df_NP$LoadedFactor))

knitr::kable(tbl4_NP)
```

```{r}
fourFL_NoNum_NP <- fourFL_df_NP[,-c(1, 16)] # removing non-numerical columns

fourFL_df_NP$firstloading <- apply(fourFL_NoNum_NP, 1, function(z) na.omit(z)[1]) # extract first loading 

fourFL_df_NP$firstloading <- as.numeric(fourFL_df_NP$firstloading) 

fourFL_df_NP$secondloading <- apply(fourFL_NoNum_NP, 1, function(z) na.omit(z)[2]) # extract second loading 

fourFL_df_NP$secondloading <- as.numeric(fourFL_df_NP$secondloading)

fourFL_df_NP$thirdloading <- apply(fourFL_NoNum_NP, 1, function(z) na.omit(z)[3]) # extract third loading

fourFL_df_NP$thirdloading <- as.numeric(fourFL_df_NP$thirdloading)

fourFL_df_NP$fourthloading <- apply(fourFL_NoNum_NP, 1, function(z) na.omit(z)[4]) # extract fourth loading

fourFL_df_NP$fourthloading <- as.numeric(fourFL_df_NP$fourthloading)

fourFL_df_NP$firstFL_inrange <- ifelse(abs(fourFL_df_NP$firstloading) >= .40 & abs(fourFL_df_NP$firstloading) < .75, TRUE, FALSE)

fourFL_df_NP$secondFL_inrange <- ifelse(abs(fourFL_df_NP$secondloading) >= .40 & abs(fourFL_df_NP$secondloading) < .75, TRUE, FALSE)

fourFL_df_NP$thirdFL_inrange<- ifelse(abs(fourFL_df_NP$thirdloading) >= .40 & abs(fourFL_df_NP$thirdloading) < .75, TRUE, FALSE)

fourFL_df_NP$fourthFL_inrange<- ifelse(abs(fourFL_df_NP$fourthloading) >= .40 & abs(fourFL_df_NP$fourthloading) < .75, TRUE, FALSE)

fourFL_df_loadings_NP <- fourFL_df_NP[,16:24]
```

```{r}
fourFL_tbl_row1_NP <- as.data.frame(fourFL_df_loadings_NP[1,])

knitr::kable(fourFL_tbl_row1_NP) # red, indicator for different subscales in different samples & in range 
```

```{r}
fourFL_tbl_row2_NP <- as.data.frame(fourFL_df_loadings_NP[2,])

knitr::kable(fourFL_tbl_row2_NP) # orange, weak loadings for different subscales in different samples 
```

```{r}
fourFL_tbl_row3_NP <- as.data.frame(fourFL_df_loadings_NP[3,])

knitr::kable(fourFL_tbl_row3_NP) # yellow, FL in range for the same factor across all 3 subscales but also .337 cross-loading for different factor in com sample 
```

```{r}
fourFL_tbl_row4_NP <- as.data.frame(fourFL_df_loadings_NP[4,])

knitr::kable(fourFL_tbl_row4_NP) # orange, weak loadings for different subscales in different samples 
```

```{r}
fourFL_tbl_row5_NP <- as.data.frame(fourFL_df_loadings_NP[5,])

knitr::kable(fourFL_tbl_row5_NP) # orange, weak loadings for different subscales in different samples 
```

```{r}
fourFL_tbl_row6_NP <- as.data.frame(fourFL_df_loadings_NP[6,])

knitr::kable(fourFL_tbl_row6_NP) # red, indicator for different subscales in different samples & in range 
```

```{r}
fourFL_tbl_row7_NP <- as.data.frame(fourFL_df_loadings_NP[7,])

knitr::kable(fourFL_tbl_row7_NP) # red, indicator for different subscales in different samples & in range 
```

```{r}
fourFL_tbl_row8_NP <- as.data.frame(fourFL_df_loadings_NP[8,])

knitr::kable(fourFL_tbl_row8_NP) # yellow, FL in range for same factor across all 3 samples but has >.75 loading for the the smu sample & has a cross-loading of <.30 for a different factor in the com sample 
```

```{r}
fourFL_tbl_row9_NP <- as.data.frame(fourFL_df_loadings_NP[9,])

knitr::kable(fourFL_tbl_row9_NP) # orange, weak loadings for different subscales in different samples 
```

```{r}
fourFL_tbl_row10_NP <- as.data.frame(fourFL_df_loadings_NP[10,])

knitr::kable(fourFL_tbl_row10_NP) # green, FL in range for same factor across all 3 samples and has <.30 cross-loading  
```

```{r}
fourFL_tbl_row11_NP <- as.data.frame(fourFL_df_loadings_NP[11,])

knitr::kable(fourFL_tbl_row11_NP) # red, indicator for different subscales in different samples & in range 
```

```{r}
fourFL_tbl_row12_NP <- as.data.frame(fourFL_df_loadings_NP[12,])

knitr::kable(fourFL_tbl_row12_NP) # orange, weak loadings for different subscales in different samples 
```

```{r}
fourFL_tbl_row13_NP <- as.data.frame(fourFL_df_loadings_NP[13,])

knitr::kable(fourFL_tbl_row13_NP) # yellow, FL in range for same factor across all 3 samples but has >.75 loading for the the smu sample & has a cross-loading of <.30 for a different factor in the smu sample 
```

```{r}
fourFL_tbl_row14_NP <- as.data.frame(fourFL_df_loadings_NP[14,])

knitr::kable(fourFL_tbl_row14_NP) # orange, weak loadings for different subscales in different samples 
```

```{r}
fourFL_tbl_row15_NP <- as.data.frame(fourFL_df_loadings_NP[15,])

knitr::kable(fourFL_tbl_row15_NP) # red, indicator for different subscales in different samples & in range 
```

```{r}
fourFL_tbl_row16_NP <- as.data.frame(fourFL_df_loadings_NP[16,])

knitr::kable(fourFL_tbl_row16_NP) # red, indicator for different subscales in different samples & in range 
```

```{r}
fourFL_tbl_row17_NP <- as.data.frame(fourFL_df_loadings_NP[17,])

knitr::kable(fourFL_tbl_row17_NP) # red, indicator for different subscales in different samples & in range 
```

```{r}
fourFL_tbl_row18_NP <- as.data.frame(fourFL_df_loadings_NP[18,])

knitr::kable(fourFL_tbl_row18_NP) # red, indicator for different subscales in different samples & in range 
```

```{r}
fourFL_tbl_row19_NP <- as.data.frame(fourFL_df_loadings_NP[19,])

knitr::kable(fourFL_tbl_row19_NP) # green, FL in range for same factor across all 3 samples and has <.30 cross-loading  
```

```{r}
# =========================================================================== GREEN 4 START 

fourFL_GREEN_NP <- fourFL_df_NP[c(10, 19), ]

fourFL_GREENitems_NP <- fourFL_GREEN_NP$Item_No

# =========================================================================== GREEN 4 END

# =========================================================================== YELLOW 5 START 

fourFL_YELLOW_NP <- fourFL_df_NP[c(3, 8, 13, 19),]

fourFL_YELLOWitems_NP <- fourFL_YELLOW_NP$Item_No

# =========================================================================== YELLOW 5 END 

# =========================================================================== ORANGE 5 START 

fourFL_ORANGE_NP <- fourFL_df_NP[c(2, 4, 5, 9, 12, 14),]

fourFL_ORANGEitems_NP <- fourFL_ORANGE_NP$Item_No

# =========================================================================== ORANGE 5 END 

# =========================================================================== RED 4 START 

fourFL_RED_NP <- fourFL_df_NP[c(1, 6, 7, 11, 15, 16, 17, 18),]

fourFL_REDitems_NP <- fourFL_RED_NP$Item_No

# =========================================================================== RED 4 END 

### FIVE FACTOR LOADINGS 

fiveFL_NP <- which(FL_count_NP == 5) # subsetting for items that loaded on five factors

fiveFL_df_NP <- Combined_Overall_NoPN[fiveFL_NP, ]

tbl5_NP <- as.data.frame(table(fiveFL_df_NP$LoadedFactor))

knitr::kable(tbl5_NP)
```

```{r}
fiveFL_NoNum_NP <- fiveFL_df_NP[,-c(1, 16)] # removing non-numerical columns

fiveFL_df_NP$firstloading <- apply(fiveFL_NoNum_NP, 1, function(z) na.omit(z)[1]) # extract first loading 

fiveFL_df_NP$firstloading <- as.numeric(fiveFL_df_NP$firstloading) 

fiveFL_df_NP$secondloading <- apply(fiveFL_NoNum_NP, 1, function(z) na.omit(z)[2]) # extract second loading 

fiveFL_df_NP$secondloading <- as.numeric(fiveFL_df_NP$secondloading)

fiveFL_df_NP$thirdloading <- apply(fiveFL_NoNum_NP, 1, function(z) na.omit(z)[3]) # extract third loading

fiveFL_df_NP$thirdloading <- as.numeric(fiveFL_df_NP$thirdloading)

fiveFL_df_NP$fourthloading <- apply(fiveFL_NoNum_NP, 1, function(z) na.omit(z)[4]) # extract fourth loading

fiveFL_df_NP$fourthloading <- as.numeric(fiveFL_df_NP$fourthloading)

fiveFL_df_NP$fifthloading <- apply(fiveFL_NoNum_NP, 1, function(z) na.omit(z)[5]) # extract fifth loading

fiveFL_df_NP$fifthloading <- as.numeric(fiveFL_df_NP$fifthloading)

fiveFL_df_NP$firstFL_inrange <- ifelse(abs(fiveFL_df_NP$firstloading) >= .40 & abs(fiveFL_df_NP$firstloading) < .75, TRUE, FALSE)

fiveFL_df_NP$secondFL_inrange <- ifelse(abs(fiveFL_df_NP$secondloading) >= .40 & abs(fiveFL_df_NP$secondloading) < .75, TRUE, FALSE)

fiveFL_df_NP$thirdFL_inrange<- ifelse(abs(fiveFL_df_NP$thirdloading) >= .40 & abs(fiveFL_df_NP$thirdloading) < .75, TRUE, FALSE)

fiveFL_df_NP$fourthFL_inrange<- ifelse(abs(fiveFL_df_NP$fourthloading) >= .40 & abs(fiveFL_df_NP$fourthloading) < .75, TRUE, FALSE)

fiveFL_df_NP$fifthFL_inrange<- ifelse(abs(fiveFL_df_NP$fifthloading) >= .40 & abs(fiveFL_df_NP$fifthloading) < .75, TRUE, FALSE)

fiveFL_df_loadings_NP <- fiveFL_df_NP[,16:26]
```

```{r}
fiveFL_tbl_row1_NP <- as.data.frame(fiveFL_df_loadings_NP[1,])

knitr::kable(fiveFL_tbl_row1_NP) # orange, weak loadings for different subscales in different samples 
```

```{r}
fiveFL_tbl_row2_NP <- as.data.frame(fiveFL_df_loadings_NP[2,])

knitr::kable(fiveFL_tbl_row2_NP) # orange, weak loadings for different subscales in different samples 
```

```{r}
fiveFL_tbl_row3_NP <- as.data.frame(fiveFL_df_loadings_NP[3,])

knitr::kable(fiveFL_tbl_row3_NP) # red, indicator for different subscales in different samples & in range 
```

```{r}
fiveFL_tbl_row4_NP <- as.data.frame(fiveFL_df_loadings_NP[4,])

knitr::kable(fiveFL_tbl_row4_NP) # red, indicator for different subscales in different samples & in range 
```

```{r}
fiveFL_tbl_row5_NP <- as.data.frame(fiveFL_df_loadings_NP[5,])

knitr::kable(fiveFL_tbl_row5_NP) # red, indicator for different subscales in different samples & in range 
```

```{r}
fiveFL_tbl_row6_NP <- as.data.frame(fiveFL_df_loadings_NP[6,])

knitr::kable(fiveFL_tbl_row6_NP) # red, indicator for different subscales in different samples & in range 
```

```{r}
# =========================================================================== ORANGE 6 START 

fiveFL_ORANGE_NP <- fiveFL_df_NP[c(1, 2),]

fiveFL_ORANGEitems_NP <- fiveFL_ORANGE_NP$Item_No

# =========================================================================== ORANGE 6 END 

# =========================================================================== RED 5 START 

fiveFL_RED_NP <- fiveFL_df_NP[c(3, 4, 5, 6),]

fiveFL_REDitems_NP <- fiveFL_RED_NP$Item_No

# =========================================================================== RED 5 END 

### SIX FACTOR LOADINGS 

sixFL_NP <- which(FL_count_NP == 6) # subsetting for items that loaded on six factors

sixFL_df_NP <- Combined_Overall_NoPN[sixFL_NP, ]

tbl6_NP <- as.data.frame(table(sixFL_df_NP$LoadedFactor))

knitr::kable(tbl6_NP)
```

```{r}
sixFL_NoNum_NP <- sixFL_df_NP[,-c(1, 16)] # removing non-numerical columns

sixFL_df_NP$firstloading <- apply(sixFL_NoNum_NP, 1, function(z) na.omit(z)[1]) # extract first loading 

sixFL_df_NP$firstloading <- as.numeric(sixFL_df_NP$firstloading) 

sixFL_df_NP$secondloading <- apply(sixFL_NoNum_NP, 1, function(z) na.omit(z)[2]) # extract second loading 

sixFL_df_NP$secondloading <- as.numeric(sixFL_df_NP$secondloading)

sixFL_df_NP$thirdloading <- apply(sixFL_NoNum_NP, 1, function(z) na.omit(z)[3]) # extract third loading

sixFL_df_NP$thirdloading <- as.numeric(sixFL_df_NP$thirdloading)

sixFL_df_NP$fourthloading <- apply(sixFL_NoNum_NP, 1, function(z) na.omit(z)[4]) # extract fourth loading

sixFL_df_NP$fourthloading <- as.numeric(sixFL_df_NP$fourthloading)

sixFL_df_NP$fifthloading <- apply(sixFL_NoNum_NP, 1, function(z) na.omit(z)[5]) # extract fifth loading

sixFL_df_NP$fifthloading <- as.numeric(sixFL_df_NP$fifthloading)

sixFL_df_NP$sixthloading <- apply(sixFL_NoNum_NP, 1, function(z) na.omit(z)[6]) # extract sixth loading

sixFL_df_NP$sixthloading <- as.numeric(sixFL_df_NP$sixthloading)

sixFL_df_NP$firstFL_inrange <- ifelse(abs(sixFL_df_NP$firstloading) >= .40 & abs(sixFL_df_NP$firstloading) < .75, TRUE, FALSE)

sixFL_df_NP$secondFL_inrange <- ifelse(abs(sixFL_df_NP$secondloading) >= .40 & abs(sixFL_df_NP$secondloading) < .75, TRUE, FALSE)

sixFL_df_NP$thirdFL_inrange<- ifelse(abs(sixFL_df_NP$thirdloading) >= .40 & abs(sixFL_df_NP$thirdloading) < .75, TRUE, FALSE)

sixFL_df_NP$fourthFL_inrange<- ifelse(abs(sixFL_df_NP$fourthloading) >= .40 & abs(sixFL_df_NP$fourthloading) < .75, TRUE, FALSE)

sixFL_df_NP$fifthFL_inrange<- ifelse(abs(sixFL_df_NP$fifthloading) >= .40 & abs(sixFL_df_NP$fifthloading) < .75, TRUE, FALSE)

sixFL_df_NP$sixthFL_inrange<- ifelse(abs(sixFL_df_NP$sixthloading) >= .40 & abs(sixFL_df_NP$sixthloading) < .75, TRUE, FALSE)

sixFL_df_loadings_NP <- sixFL_df_NP[,16:28]
```

```{r}
sixFL_tbl_row1_NP <- as.data.frame(sixFL_df_loadings_NP[1,])

knitr::kable(sixFL_tbl_row1_NP) # red, indicator for different subscales in different samples & in range 
```

```{r}
sixFL_tbl_row2_NP <- as.data.frame(sixFL_df_loadings_NP[2,])

knitr::kable(sixFL_tbl_row2_NP) # orange, indicator in range for same factor across all three samples but also has cross-loadings of .264, .251, and .343 for different factors 
```

```{r}
sixFL_tbl_row3_NP <- as.data.frame(sixFL_df_loadings_NP[3,])

knitr::kable(sixFL_tbl_row3_NP) # red, indicator for different subscales in different samples & in range 
```

```{r}
# =========================================================================== ORANGE 7 START 

sixFL_ORANGE_NP <- sixFL_df_NP[2,]

sixFL_ORANGEitems_NP <- sixFL_ORANGE_NP$Item_No

# =========================================================================== ORANGE 7 END 

# =========================================================================== RED 6 START 

sixFL_RED_NP <- sixFL_df_NP[c(1, 3),]

sixFL_REDitems_NP <- sixFL_RED_NP$Item_No

# =========================================================================== RED 6 END 

### SEVEN FACTOR LOADINGS 

sevenFL_NP <- which(FL_count_NP == 7) # subsetting for items that loaded on seven factors

sevenFL_df_NP <- Combined_Overall_NoPN[sevenFL_NP, ]

tbl7_NP <- as.data.frame(table(sevenFL_df_NP$LoadedFactor))

knitr::kable(tbl7_NP)
```

```{r}
sevenFL_NoNum_NP <- sevenFL_df_NP[,-c(1, 16)] # removing non-numerical columns

sevenFL_df_NP$firstloading <- apply(sevenFL_NoNum_NP, 1, function(z) na.omit(z)[1]) # extract first loading 

sevenFL_df_NP$firstloading <- as.numeric(sevenFL_df_NP$firstloading) 

sevenFL_df_NP$secondloading <- apply(sevenFL_NoNum_NP, 1, function(z) na.omit(z)[2]) # extract second loading 

sevenFL_df_NP$secondloading <- as.numeric(sevenFL_df_NP$secondloading)

sevenFL_df_NP$thirdloading <- apply(sevenFL_NoNum_NP, 1, function(z) na.omit(z)[3]) # extract third loading

sevenFL_df_NP$thirdloading <- as.numeric(sevenFL_df_NP$thirdloading)

sevenFL_df_NP$fourthloading <- apply(sevenFL_NoNum_NP, 1, function(z) na.omit(z)[4]) # extract fourth loading

sevenFL_df_NP$fourthloading <- as.numeric(sevenFL_df_NP$fourthloading)

sevenFL_df_NP$fifthloading <- apply(sevenFL_NoNum_NP, 1, function(z) na.omit(z)[5]) # extract fifth loading

sevenFL_df_NP$fifthloading <- as.numeric(sevenFL_df_NP$fifthloading)

sevenFL_df_NP$sixthloading <- apply(sevenFL_NoNum_NP, 1, function(z) na.omit(z)[6]) # extract sixth loading

sevenFL_df_NP$sixthloading <- as.numeric(sevenFL_df_NP$sixthloading)

sevenFL_df_NP$seventhloading <- apply(sevenFL_NoNum_NP, 1, function(z) na.omit(z)[7]) # extract seventh loading

sevenFL_df_NP$seventhloading <- as.numeric(sevenFL_df_NP$seventhloading)

sevenFL_df_NP$firstFL_inrange <- ifelse(abs(sevenFL_df_NP$firstloading) >= .40 & abs(sevenFL_df_NP$firstloading) < .75, TRUE, FALSE)

sevenFL_df_NP$secondFL_inrange <- ifelse(abs(sevenFL_df_NP$secondloading) >= .40 & abs(sevenFL_df_NP$secondloading) < .75, TRUE, FALSE)

sevenFL_df_NP$thirdFL_inrange<- ifelse(abs(sevenFL_df_NP$thirdloading) >= .40 & abs(sevenFL_df_NP$thirdloading) < .75, TRUE, FALSE)

sevenFL_df_NP$fourthFL_inrange<- ifelse(abs(sevenFL_df_NP$fourthloading) >= .40 & abs(sevenFL_df_NP$fourthloading) < .75, TRUE, FALSE)

sevenFL_df_NP$fifthFL_inrange<- ifelse(abs(sevenFL_df_NP$fifthloading) >= .40 & abs(sevenFL_df_NP$fifthloading) < .75, TRUE, FALSE)

sevenFL_df_NP$sixthFL_inrange<- ifelse(abs(sevenFL_df_NP$sixthloading) >= .40 & abs(sevenFL_df_NP$sixthloading) < .75, TRUE, FALSE)

sevenFL_df_NP$seventhFL_inrange<- ifelse(abs(sevenFL_df_NP$seventhloading) >= .40 & abs(sevenFL_df_NP$seventhloading) < .75, TRUE, FALSE)

sevenFL_df_loadings_NP <- sevenFL_df_NP[,16:30]
```

```{r}
sevenFL_tbl_row1_NP <- as.data.frame(sevenFL_df_loadings_NP[1,])

knitr::kable(sevenFL_tbl_row1_NP) # red, indicator for different subscales in different samples & in range 
```

```{r}
sevenFL_tbl_row2_NP <- as.data.frame(sevenFL_df_loadings_NP[2,])

knitr::kable(sevenFL_tbl_row2_NP) # red, indicator for different subscales in different samples & in range 
```

```{r}
# =========================================================================== RED 7 START 

sevenFL_RED_NP <- sevenFL_df_NP[c(1, 2),]

sevenFL_REDitems_NP <- sevenFL_RED_NP$Item_No

# =========================================================================== RED 7 END 

### EIGHT FACTOR LOADINGS 

eightFL_NP <- which(FL_count_NP == 8) # subsetting for items that loaded on eight factors

eightFL_df_NP <- Combined_Overall_NoPN[eightFL_NP, ]

tbl8_NP <- as.data.frame(table(eightFL_df_NP$LoadedFactor))

knitr::kable(tbl8_NP)
```

```{r}
eightFL_NoNum_NP <- eightFL_df_NP[,-c(1, 16)] # removing non-numerical columns

eightFL_df_NP$firstloading <- apply(eightFL_NoNum_NP, 1, function(z) na.omit(z)[1]) # extract first loading 

eightFL_df_NP$firstloading <- as.numeric(eightFL_df_NP$firstloading) 

eightFL_df_NP$secondloading <- apply(eightFL_NoNum_NP, 1, function(z) na.omit(z)[2]) # extract second loading 

eightFL_df_NP$secondloading <- as.numeric(eightFL_df_NP$secondloading)

eightFL_df_NP$thirdloading <- apply(eightFL_NoNum_NP, 1, function(z) na.omit(z)[3]) # extract third loading

eightFL_df_NP$thirdloading <- as.numeric(eightFL_df_NP$thirdloading)

eightFL_df_NP$fourthloading <- apply(eightFL_NoNum_NP, 1, function(z) na.omit(z)[4]) # extract fourth loading

eightFL_df_NP$fourthloading <- as.numeric(eightFL_df_NP$fourthloading)

eightFL_df_NP$fifthloading <- apply(eightFL_NoNum_NP, 1, function(z) na.omit(z)[5]) # extract fifth loading

eightFL_df_NP$fifthloading <- as.numeric(eightFL_df_NP$fifthloading)

eightFL_df_NP$sixthloading <- apply(eightFL_NoNum_NP, 1, function(z) na.omit(z)[6]) # extract sixth loading

eightFL_df_NP$sixthloading <- as.numeric(eightFL_df_NP$sixthloading)

eightFL_df_NP$seventhloading <- apply(eightFL_NoNum_NP, 1, function(z) na.omit(z)[7]) # extract seventh loading

eightFL_df_NP$seventhloading <- as.numeric(eightFL_df_NP$seventhloading)

eightFL_df_NP$eighthloading <- apply(eightFL_NoNum_NP, 1, function(z) na.omit(z)[8]) # extract eighth loading

eightFL_df_NP$eighthloading <- as.numeric(eightFL_df_NP$eighthloading)

eightFL_df_NP$firstFL_inrange <- ifelse(abs(eightFL_df_NP$firstloading) >= .40 & abs(eightFL_df_NP$firstloading) < .75, TRUE, FALSE)

eightFL_df_NP$secondFL_inrange <- ifelse(abs(eightFL_df_NP$secondloading) >= .40 & abs(eightFL_df_NP$secondloading) < .75, TRUE, FALSE)

eightFL_df_NP$thirdFL_inrange<- ifelse(abs(eightFL_df_NP$thirdloading) >= .40 & abs(eightFL_df_NP$thirdloading) < .75, TRUE, FALSE)

eightFL_df_NP$fourthFL_inrange<- ifelse(abs(eightFL_df_NP$fourthloading) >= .40 & abs(eightFL_df_NP$fourthloading) < .75, TRUE, FALSE)

eightFL_df_NP$fifthFL_inrange<- ifelse(abs(eightFL_df_NP$fifthloading) >= .40 & abs(eightFL_df_NP$fifthloading) < .75, TRUE, FALSE)

eightFL_df_NP$sixthFL_inrange<- ifelse(abs(eightFL_df_NP$sixthloading) >= .40 & abs(eightFL_df_NP$sixthloading) < .75, TRUE, FALSE)

eightFL_df_NP$seventhFL_inrange<- ifelse(abs(eightFL_df_NP$seventhloading) >= .40 & abs(eightFL_df_NP$seventhloading) < .75, TRUE, FALSE)

eightFL_df_NP$eighthFL_inrange <- ifelse(abs(eightFL_df_NP$eighthloading) >= .40 & abs(eightFL_df_NP$eighthloading) < .75, TRUE, FALSE)

eightFL_df_loadings_NP <- eightFL_df_NP[,16:32]
```

```{r}
eightFL_tbl_row1_NP <- as.data.frame(eightFL_df_loadings_NP[1,])

knitr::kable(eightFL_tbl_row1_NP) # red, indicator for different subscales in different samples & in range 
```

```{r}
# =========================================================================== RED 8 START 

eightFL_RED_NP <- eightFL_df_NP[1,]

eightFL_REDitems_NP <- eightFL_RED_NP$Item_No

# =========================================================================== RED 8 END 
```

```{r}
red_list_NP <- sort(c(zeroFL_NP, twoFL_SP_REDitems_NP, threeFL_REDitems_NP, fourFL_REDitems_NP, fiveFL_REDitems_NP, sixFL_REDitems_NP, sevenFL_REDitems_NP, eightFL_REDitems_NP))

orange_list_NP <- sort(c(oneFL_notir_items_NP, twoFL_NS_ORANGEitems_NP, twoFL_SP_ORANGEitems_NP, threeFL_ORANGEitems_NP, fourFL_ORANGEitems_NP, fiveFL_ORANGEitems_NP, sixFL_ORANGEitems_NP))

yellow_list_NP <- sort(c(oneFL_inrange_items_NP, twoFL_NS_YELLOWitems_NP, twoFL_SP_YELLOWitems_NP, threeFL_YELLOWitems_NP, fourFL_YELLOWitems_NP))

green_list_NP <- sort(c(twoFL_NS_GREENitems_NP, threeFL_GREENitems_NP, fourFL_GREENitems_NP))

``` 

```{r}
Combined_Overall_NoPN$category <- ifelse(Combined_Overall_NoPN$Item_No %in% red_list_NP, 1, ifelse(Combined_Overall_NoPN$Item_No %in% orange_list_NP, 2, ifelse(Combined_Overall_NoPN$Item_No %in% yellow_list_NP, 3, ifelse(Combined_Overall_NoPN$Item_No %in% green_list_NP, 4, 5))))

Combined_Overall_NoPN$Item <- item_list$X1

Combined_Overall_NoPN <- Combined_Overall_NoPN[ ,c(1, 18, 2:17)]

knitr::kable(Combined_Overall_NoPN, booktabs = TRUE) %>%
  column_spec(1:18, color = "black", background = spec_color2(Combined_Overall_NoPN$category, palette = my_backgrounds)) %>%
  kable_styling(position="center") %>%
  scroll_box(height = "300px")  
```

### Results Overview 

```{r}
knitr::kable(Combined_Overall_PN, booktabs = TRUE) %>%
  column_spec(1:12, color = "black", background = spec_color2(Combined_Overall_PN$category, palette = my_backgrounds)) %>%
  kable_styling(position="center") %>%
  scroll_box(height = "300px")  
```

- Positive Valence Subscale
<font color = 'green'>
  + Item 11 (green): Most of the time, I feel a sense of achievement right after I do physical activity.
  + Item 19 (green): In most cases, I feel healthier right after I do physical activity.
  + Item 22 (green): I've experienced that consistent physical activity helps me manage my stress.
  + Item 26 (green): When I am exercising regularly, I've noticed my health improves.
  + Item 41 (green): I often feel good about myself after doing physical activity.
  + Item 56 (green): I am more physically attractive when I exercise often.
  + Item 58 (green): I recognize when my abilities improve during physical activity.
  + Item 63 (green): During physical activity, I've noticed my body feels stronger.
  + Item 83 (green): When I do physical activity regularly, I've found my weight is easier to control.
  + Item 84 (green): I feel sexier when I workout frequently.
  + Item 86 (green): When I workout consistently, I have noticed my performance during workouts improves.
  + Item 113 (green): When I exercise consistently, I notice my self-esteem improves.
  + Item 118 (green): I'm happy after physical activity.
  + Item 139 (green): I've found that working out frequently makes it easier to do other physical things.
  + Item 141 (green): I feel like I've achieved a lot when I maintain a physical activity routine.
  + Item 142 (green): During my workouts, I've noticed when my skills have improved.
  + Item 143 (green): When I am getting regular physical activity, I feel like I am the best version of me.
  + Item 167 (green): When I'm doing regular physical activity, I experience fewer health problems.
  + Item 169 (green): When I work out frequently, I have much greater respect for myself.
  + Item 175 (green): I usually feel more physically fit after completing an exercise session.
  + Item 191 (green): I feel in much better shape when I routinely workout.
  + Item 193 (green): Working out regularly makes me feel more satisfied with myself.
  + Item 203 (green): After I finish an exercise session, I frequently feel greater respect for myself.
  + Item 206 (green): After physical activity, I often notice myself thinking that I have improved my physical(?)
  + Item 209 (green): I really notice how much better I feel when I exercise consistently.
  + Item 215 (green): When I maintain an exercise routine, I find I am more content with myself.
  + Item 232 (green): When I workout consistently, I notice my physical strength improves a lot.
  + Item 234 (green): I tend to notice when physical activity becomes easier for me.
  + Item 236 (green): I usually feel a sense of pride after I do physical activity.
  + Item 239 (green): I notice I feel more at ease around others when I keep an exercise routine.
  + Item 241 (green): I have found my self-esteem improves right after I am physically active.
  + Item 248 (green): I have noticed I feel a lot healthier when I engage in regular physical activity.
  + Item 249 (green): When I workout frequently, I see my muscles become much more defined.
  + Item 264 (green): I have a lot more physical endurance and stamina when I work out c(?)
  + Item 266 (green): When I am exercising regularly, I notice I am much more confident in my exercise abilities.
  + Item 280 (green): I frequently feel good after physical activity.
  + Item 301 (green): In my experience, I am able to perform daily activities more easily when I exercise consistently.
  + Item 305 (green): I feel great when I'm engaging in physical activity. 
</font>
<font color = 'gray'>
  + Item 7 (yellow): During a workout, I get needed time to myself.
  + Item 15 (yellow): After an exercise session, I feel more attractive.
  + Item 28 (yellow): When I am working out on a regular basis, I often feel a sense of pride.
  + Item 44 (yellow): I am usually comfortable with my appearance when I workout.
  + Item 48 (yellow): Following each workout, I think about how I helped manage my weight.
  + Item 51 (yellow): I have found that I'm less anxious when I workout consistently.
  + Item 52 (yellow): My focus improves when I'm in a workout session. 
  + Item 53 (yellow): After physical activity, my mind is clearer. 
  + Item 54 (yellow): I've noticed regular physical activity keeps my mind sharp. 
  + Item 55 (yellow):  When I exercise consistently, I've noticed my physical fitness improves.
  + Item 76 (yellow): Following my exercise sessions, I often think about progress I've made toward my health
  + Item 82 (yellow): My focus is better when I exercise frequently.
  + Item 85 (yellow): I feel good about myself when I do regular physical activity.
  + Item 89 (yellow): When I'm in a workout session, I am less tense.
  + Item 90 (yellow): After I exercise, I feel calm. 
  + Item 98 (yellow): After a workout, I usually feel like I accomplished a lot.
  + Item 104 (yellow):Immediately after working out, I think about the positive effects on my health.
  + Item 107 (yellow): When I exercise on a regular basis, I've found that I have more energy.
  + Item 111 (yellow): When I exercise often, I get better sleep.
  + Item 112 (yellow): When I get regular physical activity, I notice my body is more toned.
  + Item 114 (yellow): During a workout, it's easy for me to tell when I am doing it well.
  + Item 115 (yellow): When I workout consistently, I see myself as an "exerciser". 
  + Item 116 (yellow): When I'm exercising, time flies. 
  + Item 135 (yellow): When I am exercising regularly, I typically feel more calm.
  + Item 136 (yellow): I find it easier to make important decisions during physical activity.
  + Item 140 (yellow): My clothes fit better when I am consistently exercising.
  + Item 151 (yellow): During a workout, I get a break from other people.
  + Item 157 (yellow): I've noticed parts of my body look better after an exercise session.
  + Item 163 (yellow): When I work out often, I've found my life is easier to deal with.
  + Item 164 (yellow): During a workout session, good ideas often come to mind.
  + Item 168 (yellow): When I am doing routine physical activity, I can see how much better my body looks.
  + Item 173 (yellow): I feel I have accomplished a lot after I exercise.
  + Item 177 (yellow): My doctor is less concerned about my health when I workout frequently.
  + Item 179 (yellow): I feel much more confident about myself during my workouts.
  + Item 180 (yellow): I am very proud of myself after I workout.
  + Item 184 (yellow): When I'm done working out, I think about the progress I've made toward living. 
  + Item 187 (yellow): When I do regular physical activity, I find daily activities are more enjoyable.
  + Item 188 (yellow): I get better perspective on problems while I workout.
  + Item 192 (yellow): Regular physical activity keeps me looking young.
  + Item 196 (yellow): During exercise, I become less anxious.
  + Item 197 (yellow): After I exercise, I feel at peace.
  + Item 202 (yellow): While working out, I'm filled with a sense of pride.
  + Item 210 (yellow): During physical activity, I come up with new solutions to things.
  + Item 212 (yellow): I experience much less mental fatigue when I workout frequently.
  + Item 213 (yellow): I've noticed that my body is a lot more flexible when I exercise regularly.
  + Item 214 (yellow): When I exercise consistently, my skin looks better.
  + Item 216 (yellow): When I am exercising regularly, I've noticed my exercise abilities get much better.
  + Item 225 (yellow): During my workouts, I often think about how I am improving my physical fitness.
  + Item 229 (yellow): My awareness is improved while I exercise.
  + Item 238 (yellow): I normally feel strong when I finish my workouts.
  + Item 259 (yellow): After a workout, I think about how I am delaying dementia.
  + Item 263 (yellow): I've noticed my mental performance improves a lot when I workout regularly.
  + Item 268 (yellow): Most of the time, finishing a workout leaves me feeling refreshed.
  + Item 275 (yellow): I find I'm less forgetful after a workout session.
  + Item 277 (yellow): Certain parts of my body look noticeably better when I exercise consistently.
  + Item 294 (yellow): I have found I'm much less stressed after physical activity.
  + Item 300 (yellow): While I workout, my body's flexibility improves a lot. 
  + Item 304 (yellow): When I do physical activity regularly, my body functions significantly better.
  + Item 306 (yellow): I often feel inspired after I exercise.
  + Item 308 (yellow): I'm a lot less anxious after physical activity. 
  + Item 310 (yellow): I am noticeably less irritable after I exercise. 
  + Item 312 (yellow): I'm usually less tense after physical activity. 
  </font>

- Negative Valence Subscale
<font color = 'green'>
  + Item 40 (green): Sometimes I feel useless during exercise.
  + Item 147 (green): My body feels tense during physical activity.
  + Item 244 (green): When I'm exercising, I feel guilty that I'm not doing other things I should be doing.
  + Item 245 (green): I find maintaining an exercise routine makes me annoyed.
  + Item 288 (green): I sometimes get discouraged during physical activity.
</font>
<font color = 'gray'>
  + Item 8 (yellow): I catch myself trying to outdo others during physical activity.
  + Item 9 (yellow): I notice that other people seem to do better than me when I do my workout sessions.
  + Item 10 (yellow): I feel unattractive when I'm doing physical activity.
  + Item 13 (yellow): While I'm working out, I think about how bad I smell.
  + Item 34 (yellow): I am physically uncomfortable during exercise.
  + Item 37 (yellow): I find myself trying to meet others expectations during physical activity.
  + Item 49 (yellow): I've noticed exercise takes too much time away from other activities.
  + Item 62 (yellow): I feel emotionally drained when I finish a workout.
  + Item 69 (yellow): I sometimes feel like a failure when I exercise.
  + Item 102 (yellow): After a workout, I often notice I look like a mess.
  + Item 134 (yellow): I am uncomfortable in my workout location.
  + Item 153 (yellow): I feel awkward while I work out.
  + Item 154 (yellow): I am critical of myself after finishing a workout.
  + Item 161 (yellow): I've noticed that working out requires too much energy.
  + Item 178 (yellow): I find myself hoping to outperform others during exercise sessions.
  + Item 205 (yellow): I aggravate a health condition when I exercise.
  + Item 207 (yellow): In my experience, planning/scheduling exercise is too much of a hassle.
  + Item 218 (yellow): I hate exercise while I'm doing it.
  + Item 220 (yellow): When I workout, I find it hard to do the right movements.
  + Item 221 (yellow): I am sleepy after my workouts.
  + Item 223 (yellow): I am embarrassed when I workout.
  + Item 227 (yellow): I've noticed that exercise is inconvenient for me.
  + Item 228 (yellow): Keeping an exercise routine stresses me out. 
  + Item 237 (yellow): I find it difficult to keep up physically with others during exercise.
  + Item 240 (yellow): I feel uncomfortable when I exercise around others.
  + Item 251 (yellow): I sometimes feel sad while I exercise.
  + Item 256 (yellow): During physical activity, I feel self-conscious.
  + Item 257 (yellow): After I workout, I feel I didn't do it well enough. 
  + Item 267 (yellow): I sometimes get frustrated during my workouts.
  + Item 271 (yellow): After I exercise, I sometimes feel like I failed.
  + Item 281 (yellow): While I exercise, I'm concerned about falling.
  + Item 286 (yellow): My joints ache more when I exercise regularly.
  + Item 290 (yellow): During a workout session, I think about the possibility of getting hurt.
  + Item 292 (yellow): I've experienced more injuries when I workout consistently.
  + Item 293 (yellow): At times, I am annoyed during exercise.
  + Item 295 (yellow): While I'm exercising, my chest feels tight. 
  + Item 297 (yellow): Being physically active on a regular basis makes my body sore. 
  + Item 298 (yellow): I occasionally feel ashamed while exercising. 
  + Item 302 (yellow): Working out is stressful while doing it. 
  + Item 309 (yellow): After a workout, I occasionally feel disappointed. 
  </font>

```{r}
knitr::kable(Combined_Overall_NoPN, booktabs = TRUE) %>%
  column_spec(1:18, color = "black", background = spec_color2(Combined_Overall_NoPN$category, palette = my_backgrounds)) %>%
  kable_styling(position="center") %>%
  scroll_box(height = "300px")  
```
 
- Flow/Mindfulness Subscale 
  <font color = 'green'>
  + Item 31 (green): While I am doing physical activity, I find myself totally engaged in the moment.
  + Item 170 (green): I find myself enjoying the challenge of my workouts.
  + Item 217 (green): I find it easy to stay focused on my workouts while I'm doing them.
  </font> 
  <font color = 'gray'>
  + Item 21 (yellow): I enjoy the setting(s) I exercise in.
  + Item 50 (yellow): I usually find the location(s) where I workout (e.g., nature, gym, home) to be pleasant. 
  + Item 61 (yellow): I feel energetic during a workout. 
  + Item 78 (yellow): I like the atmosphere of where I exercise. 
  + Item 162 (yellow):I really enjoy the surroundings I do physical activity in.
  </font> 
- Negative Appearance Subscale 
  <font color = 'green'>
  + Item 13 (green): While I'm working out, I think about how bad I smell. 
  + Item 46 (green): After exercising, I notice how bad I smell. 
  </font> 
  <font color = 'gray'>
  + Item 128 (yellow): I notice that I look sweaty during physical activity.
  + Item 256 (yellow): During physical activity, I feel self-conscious.
  + Item 298 (yellow): I occasionally feel ashamed while exercising.
  </font> 
- Positive Appearance Subscale 
  <font color = 'green'>
  + Item 15 (green): After an exercise session, I feel more attractive. 
  + Item 65 (green): I spend time with my partner/spouse while I workout. 
  + Item 71 (green): During physical activity, I notice how toned I look. 
  + Item 73 (green): When I'm done working out, I notice how toned my body looks.
  + Item 101 (green): I often think about how great I look after my workouts.
  + Item 127 (green): I feel attractive when I'm exercising. 
  + Item 129 (green): I frequently get compliments on my appearance after my workouts.
  </font> 
  <font color = 'gray'>
  + Item 12 (yellow): During my workouts, I think about how good I look. 
  + Item 42 (yellow): I like people checking me out when I exercise.
  + Item 45 (yellow): After doing physical activity, I think about how sexy I look. 
  + Item 99 (yellow): During a workout, I think about how sexy I look.
  + Item 157 (yellow): I've noticed parts of my body look better after an exercise session.
  + Item 181 (yellow): I think I look amazing while I workout.
  + Item 282 (yellow): After doing physical activity, I notice an immediate improvement in my muscle tone.
  </font> 
- Progress/Improvement Subscale
  <font color = 'green'>
  + Item 18 (green): During physical activity, I often find myself thinking about how it improves my health.
  + Item 47 (green): During a workout session, I often think about how I am preventing future health problems.
  + Item 75 (green): I frequently think about how physical activity is good for me while I do it. 
  + Item 103 (green): While working out, I'm usually thinking about my health goals. 
  + Item 104 (green): Immediately after working out, I think about the positive effects on my health.
  + Item 132 (green): I think about how exercise improves my health after most workouts.
  + Item 159 (green): During a workout, I often think about the progress I am making toward a healthier lifestyle.
  + Item 160 (green): After a workout, the fact that I am preventing future health problems is on my mind.
  + Item 184 (green): When I'm done working out, I think about the progress I've made toward living.
  + Item 242 (green): During exercise, I normally think about how it's helping me live a long and healthy life.
  + Item 283 (green): While I workout, I think about how I'm improving my heart health.
  </font> 
  <font color = 'gray'>
  + Item 76 (yellow): Following my exercise sessions, I often think about progress I've made toward my health. 
  + Item 183 (yellow): While exercising, I feel like I am managing my health status (e.g., medical conditions, illness, injuries, pain).
  + Item 225 (yellow):  During my workouts, I often think about how I am improving my physical fitness.
  + Item 273 (yellow): After physical activity, I often think about how I've improved my heart health.
  </font> 
- Physical Pain and Fatigue Subscale 
  <font color = 'gray'>
  + Item 3 (yellow): It hurts while I workout. 
  + (Reverse) Item 33 (yellow): I am full of energy after physical activity. 
  + Item 64 (yellow): I am tired after physical activity. 
  + Item 92 (yellow): My body hurts after physical activity. 
  + Item 120 (yellow): I'm sore after I exercise. 
  + Item 174 (yellow): While I do physical activity, I feel exhausted.
  + Item 198 (yellow): While I'm exercising, I find it physically difficult.
  + Item 199 (yellow): My body is fatigued after a workout.
  + Item 205 (yellow): I aggravate a health condition when I exercise. 
  + Item 253 (yellow): When I workout, I feel pain.
  + Item 254 (yellow): I am worn out after I exercise.
  + Item 269 (yellow): When I do physical activity, I feel short of breath.
  + Item 270 (yellow): I am often in pain after a workout.
  + Item 285 (yellow): I've noticed working out often makes me tired.
  + Item 286 (yellow): My joints ache more when I exercise regularly.
  + Item 289 (yellow): I feel awful at times after I do physical activity.
  + Item 307 (yellow): During exercise, I feel exhausted.
  </font> 
- Cognitive Effects/Improvements Subscale 
  <font color = 'green'>
  + Item 52 (green): My focus improves when I'm in a workout session.
  </font> 
  <font color = 'gray'>
  + Item 22 (yellow): I've experienced that consistent physical activity helps me manage my stress.
  + Item 25 (yellow): When I workout regularly, my ability to pay attention is better. 
  + Item 51 (yellow): I have found that I'm less anxious when I workout consistently. 
  + Item 53 (yellow): After physical activity, my mind is clearer. 
  + Item 54 (yellow): I've noticed regularly physical activity keeps my mind sharp. 
  + Item 79 (yellow): I've noticed that my mood is better when I engage in regular physical activity.
  + Item 80 (yellow): My mind works faster during exercise. 
  + Item 81 (yellow): I notice my focus is better after I exercise. 
  + Item 82 (yellow): My focus is better when I exercise frequently. 
  + Item 89 (yellow): When I'm in a workout session, I am less tense.   
  + Item 90 (yellow): After I exercise, I feel calm.
  + Item 109 (yellow): I can think more quickly after being physically active.
  + Item 135 (yellow): When I am exercising regularly, I typically feel more calm.
  + Item 136 (yellow): I find it easier to make important decisions during physical activity.
  + Item 137 (yellow): My thoughts are more organized after I workout.
  + Item 138 (yellow): When I get regular physical activity, my mind seems to work better.
  + Item 163 (yellow): When I work out often, I've found my life is easier to deal with.
  + Item 164 (yellow): During a workout session, good ideas often come to mind.
  + Item 165 (yellow): I am less distracted after being physically active.
  + Item 166 (yellow): I'm less distracted in my day-to-day life when I exercise consistently.
  + Item 187 (yellow): When I do regular physical activity, I find daily activities are more enjoyable.
  + Item 188 (yellow): I get better perspective on problems while I workout.
  + Item 189 (yellow): I've noticed that I can make decisions more easily after a workout.
  + Item 190 (yellow): I make better decisions when I workout routinely.
  + Item 196 (yellow): During exercise, I become less anxious.
  + Item 197 (yellow): After I exercise, I feel at peace.
  + Item 210 (yellow): During physical activity, I come up with new solutions to things.
  + Item 211 (yellow): After being physically active, I make better decisions.
  + Item 212 (yellow): I experience much less mental fatigue when I workout frequently.
  + Item 229 (yellow): My awareness is improved while I exercise.
  + Item 230 (yellow): After I finish a workout, I have more mental energy.
  + Item 231 (yellow): When I engage in regular physical activity, my ability to solve difficult problems improves.
  + Item 246 (yellow): It's easier to solve difficult problems after exercising.
  + Item 247 (yellow): My memory is better when I engage in frequent physical activity.
  + Item 261 (yellow): I've noticed more peace in my life when I workout regularly.
  + Item 263 (yellow): I've noticed my mental performance improves a lot when I workout regularly.
  + Item 279 (yellow): I find I'm less forgetful after a workout session.
  + Item 291 (yellow): I notice a lot less stress in my life when I workout regularly.
  + Item 294 (yellow): I have found I'm much less stressed after physical activity.
  + Item 296 (yellow): I'm noticeably less depressed when I do physical activity regularly.
  + Item 307 (yellow): I'm a lot less anxious after physical activity.
  + Item 310 (yellow): I am noticeably less irritable after I exercise.
  </font>
  